### 2019-03-13 streaming_data_marketplace.tex
Add FTC template

\documentclass{svproc}

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\def\UrlFont{\rmfamily}

\begin{document}
\mainmatter              % start of a contribution
%
\title{Data Marketplace for Streaming Data}
%
\titlerunning{Streaming Data Marketplace}  % abbreviated title (for running head)
%
\author{Ching-Chun Huang \and Jing-Hua Lin
}
%
\authorrunning{Ching-Chun Huang et al.} % abbreviated author list (for running head)
\tocauthor{Ching-Chun Huang, Jing-Hua Lin}
%
\institute{Cheng-Kung University, Tainan, Taiwan,\\
\email{jserv.tw@gmail.com}
}

\maketitle              % typeset the title of the contribution

%at least 70 words, at most 150 words
%It will be set in 9-point font size and be inset 1.0 cm from the right and left margins.
\begin{abstract}
abstract here
\keywords{streaming data, crowd sensing, data marketplace}
\end{abstract}

\section{Introduction}

\section{Related Work}

% ---- Bibliography ----
\begin{thebibliography}{1}
%
%\bibitem {smit:wat}
%Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
%J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}

\end{thebibliography}
\end{document}

### 2019-03-31 streaming_data_marketplace.tex
Add related work

@@
 %
-\author{Ching-Chun Huang \and Jing-Hua Lin
+\author{Ching-Chun Huang \and Ching-Hua Lin
 }
@@
 \authorrunning{Ching-Chun Huang et al.} % abbreviated author list (for running head)
-\tocauthor{Ching-Chun Huang, Jing-Hua Lin}
+\tocauthor{Ching-Chun Huang, Ching-Hua Lin}
 %
-\institute{Cheng-Kung University, Tainan, Taiwan,\\
-\email{jserv.tw@gmail.com}
+\institute{National Cheng Kung University, Taiwan\\
+\email{jserv.tw@gmail.com, jkrvivian@gmail.com}
 }
@@
 \section{Related Work}
+The increasing IoT devices brings a huge amount of data, the economic value becomes essential for parties intended to sell, buy and find data.
+The need for IoT data marketplace arises due to this.
+Recent years, several researchers has started to explore based on this concept.
+There are some critical issues need to be resolved in the design of data marketplace platform, in this paper, we focus on two issues, data integrity and the trading behavior.
+
+To ensure data integrity for IoT applications is always a challenge because of the unstandardize data format and dynamic nature.
+Moreover, the Third Party Auditors (TPAs)-based frameworks is far from being satisfactory.
+Therefore a decentralized data integrity validation has been proposed recent years, and blockchain is considered a solution.
+
+Data Integrity as a Service (DIaas) is a blockchain based framework for data integrity proposed by Bin Liu\cite{DIaas}.
+DIaas is a Cloud Server Service (CSS) for IoT dynamic data that allows both data owner and data consumer to validate data integrity by comparing hashes on smart contract  and on Cloud Server.
+Besides, smart contract can also realize the purchase agreement, including authorizing data consumer for specific data set and even the penalty for data provider if they fail to provide the data integrity.
+However, the performance analysis shows that IoT devices still have low efficiency interacting with Etheruem, this may fall to the Proof-of-Work (PoW) process is time-consuming for an IoT device and the blockchain consensus can not be reached within a short time, while Ethereum is expected to enable consensus within 12-second but the time is still longer when the authors wrote the paper.
+
+By solving the inefficiencies of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry or Web 3.0 based on the revolutionary distributed ledger technology, the \textbf{Tangle}.
+It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction.
+On top of that, Masked Authenticated Messaging(MAM)\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public.
+On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM.
+But only the data buyout doesn't meet the need of the real world, such as data subscription and a specific time period of data maybe needed for different uses.
+Moreover, even though IOTA needs less computing power than other blockchain system, doing PoW and unstable network environment are still the bottleneck for low-level devices, it may take 2 or more minutes to issue a transaction to Tangle under MAM protocol.
+
+Our proposed framework is developed based on IOTA Data Marketplace.
+We aim to solve the efficiency and reliability issue for low-level devices in blockchain system and to make the buying and selling process closer to real world that meet actual needs and usages.
 
 % ---- Bibliography ----
-\begin{thebibliography}{1}
+\begin{thebibliography}{3}
 %
-%\bibitem {smit:wat}
-%Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
-%J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}
+\bibitem {DIaas}
+Bin Liu, Xiao Liang Yu, Shiping Chen, Xiwei Xu and Liming Zhu. 
+Blockchain based Data Integrity Service Framework for IoT data. In IEEE 24th International Conference on Web Services 2017.
+
+\bibitem {IOTAwhitepaper}
+S. Popov. Iota whitepaper. Technical White Paper. 2017
+
+\bibitem {MAM}
+Paul Handy. Masked Authenticated Messaging. Medium. 2017
+\url https://blog.iota.org/introducing-masked-authenticated-messaging-e55c1822d50e
 

### 2019-08-10 paper.tex
Apply to IEEE latex template

--- 2019-03-31 streaming_data_marketplace.tex
@@
-\documentclass{svproc}
+\documentclass[journal,a4paper]{IEEEtran}
 
 % to typeset URLs, URIs, and DOIs
+\usepackage[english]{babel}
 \usepackage{url}
-\def\UrlFont{\rmfamily}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{url,hyperref,graphicx,float,times}
+\usepackage{textcomp}
+\usepackage{cite}
+\usepackage[caption=false,font=footnotesize]{subfig}
 
 \begin{document}
-\mainmatter              % start of a contribution
 %
-\title{Data Marketplace for Streaming Data}
+\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
 %
-\titlerunning{Streaming Data Marketplace}  % abbreviated title (for running head)
-%
-\author{Ching-Chun Huang \and Ching-Hua Lin
-}
-%
-\authorrunning{Ching-Chun Huang et al.} % abbreviated author list (for running head)
-\tocauthor{Ching-Chun Huang, Ching-Hua Lin}
-%
-\institute{National Cheng Kung University, Taiwan\\
-\email{jserv.tw@gmail.com, jkrvivian@gmail.com}
+\author{
+%%% Fill in name here
+\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}} \\
+
+%%% Fill in school here
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
+
+%%% Fill in address here
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road} \\
+
+%%% Fill in city and country here
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.)} \\
+
+%%% Fill in email here
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv.tw@gmail.com, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
 }
 
-\maketitle              % typeset the title of the contribution
+%
 
-%at least 70 words, at most 150 words
-%It will be set in 9-point font size and be inset 1.0 cm from the right and left margins.
+\maketitle              
+% 50-80 words
 \begin{abstract}
 abstract here
-\keywords{streaming data, crowd sensing, data marketplace}
 \end{abstract}
+
+% 3 - 4 keywords
+\begin{IEEEkeywords}
+streaming data, crowd sensing, data marketplace, decentralization
+\end{IEEEkeywords}
 
@@
 
+\section{System Architecture}
+
+\section{Trading Model}
+
+\section{Conclusion}
+
 % ---- Bibliography ----
-\begin{thebibliography}{3}
-%
-\bibitem {DIaas}
-Bin Liu, Xiao Liang Yu, Shiping Chen, Xiwei Xu and Liming Zhu. 
-Blockchain based Data Integrity Service Framework for IoT data. In IEEE 24th International Conference on Web Services 2017.
+\bibliographystyle{IEEEtran}
+\bibliography{references}
 
-\bibitem {IOTAwhitepaper}
-S. Popov. Iota whitepaper. Technical White Paper. 2017
-
-\bibitem {MAM}
-Paul Handy. Masked Authenticated Messaging. Medium. 2017
-\url https://blog.iota.org/introducing-masked-authenticated-messaging-e55c1822d50e
-
-\end{thebibliography}
 \end{document}

### 2019-08-26 paper.tex
Add the 3-tier data marketplace description to related work

@@
 It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction.
-On top of that, Masked Authenticated Messaging(MAM)\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public.
+On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public.
 On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM.
@@
 
-Our proposed framework is developed based on IOTA Data Marketplace.
-We aim to solve the efficiency and reliability issue for low-level devices in blockchain system and to make the buying and selling process closer to real world that meet actual needs and usages.
+A different framework design proposed by Pooja Gupta, Salil S.Kanhere and Raja Jurdak\cite{3tierDataMarket} could solve the efficiency problem as mentioned.
+The infrastructure is a 3-tier decentralized data marketplace architectural design with smart contract which consists of provider, consumer and broker.
+Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers.
+However, there are some potential threats need to be resolved, such as payment fairness, authentication of the participants, faithful delivery of data and probable malicious behaviour of data marketplace participants.
+
+Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers.
+In our infrastructure, the identity of each participants could be easily verified with a self-soverign identity system, also we design the refunding mechanism to protect the payment fairness.
+Moreover, with MAM as our data storage on IOTA, data could be delivered securely and faithfully without any third-parties.
 

### 2019-08-27 paper.tex
Add participants

@@
 \section{System Architecture}
+\subsection{Participants}
+There are four major roles in the decentralized data marketplace.
+
+\subsubsection{Registrar}
+Registrar is responsible for creating the Registration Contract and adding new data providers, consumers and brokers to the decentralized data marketplace.
+
+\subsubsection{Provider}
+Data providers are sensor owners who are willing to sell sensing data to consumers.
+They decide the subscription period, subscription price, data type, sampling frequency.
+Afterward, they can launch the product on the decentralized data marketplace.
+Next, they collect the raw data with their sensors and send it to the broker who will assist in uploading it to the network.
+A MAM channel\cite{MAM} is used to store the encrypted data stream.
+
+\subsubsection{Consumer}
+Consumers aspire to obtain IoT data to promote the value of their service.
+However, it is a big challenge for most consumers to collect the desired data by themselves.
+So they look forward to purchasing the IoT data from data providers.
+
+\subsubsection{Broker}
+Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power.
+Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a Product Contract and upload this product to the IPFS (InterPlanetary File System)\cite{IPFS}.
+Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption.
+Then the broker provides the matching service for data provider’s products and consumer’s queries.
+After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
 

### 2019-08-27 paper.tex
Add Component - IOTA

@@
 \subsubsection{Registrar}
-Registrar is responsible for creating the Registration Contract and adding new data providers, consumers and brokers to the decentralized data marketplace.
+Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
 
-\subsubsection{Provider}
-Data providers are sensor owners who are willing to sell sensing data to consumers.
+\subsubsection{Data Provider}
+Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers.
 They decide the subscription period, subscription price, data type, sampling frequency.
 Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect the raw data with their sensors and send it to the broker who will assist in uploading it to the network.
-A MAM channel\cite{MAM} is used to store the encrypted data stream.
+Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network.
+An MAM channel\cite{MAM} is used to store encrypted data stream.
 
@@
 Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power.
-Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a Product Contract and upload this product to the IPFS (InterPlanetary File System)\cite{IPFS}.
+Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to the IPFS (InterPlanetary File System)\cite{IPFS}.
 Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption.
@@
 After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+
+\subsection{Component}
+\subsubsection{IOTA}
+IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
+To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions.
+Since every actor in Tangle has the same role, there is no need to offer transaction fees.
+Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions.
+Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.
+
+\subsubsection{smart contract}
+
+\subsubsection{IPFS}
+
+\subsubsection{MAM}
+
+\subsubsection{TangleID}
+
+\subsubsection{blind signature}
 

### 2019-08-27 paper.tex
Add Component - Smart Contract

@@
 \subsubsection{smart contract}
+Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
+The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency.
+All conditions and states established in the contract are transparent and with enforcement.
+The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
 

### 2019-08-27 paper.tex
Add Component - MAM

@@
 
-\subsubsection{MAM}
+\subsubsection{Masked Authenticated Messaging}
+MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network.
+The consensus algorithm of IOTA ensures data integrity.
+These properties allow MAM to meet the requirements of both data integrity and privacy.
+
+IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used.
+However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only.
+Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private.
+In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.
 

### 2019-08-27 paper.tex
Edit participants

--- 2019-08-27 paper.tex
@@
 \subsubsection{Registrar}
-Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
+Registrar is responsible for creating a Registration Contract, which preserves a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
 
@@
 Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network.
-An MAM channel\cite{MAM} is used to store encrypted data stream.
+Next, they collect raw data with their sensors and send it to the broker who will assist in uploading it to the network.
+A MAM channel\cite{MAM} is used to store  encrypted data stream.
 
@@
 
-\subsection{Component}
-\subsubsection{IOTA}
-IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
-To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions.
-Since every actor in Tangle has the same role, there is no need to offer transaction fees.
-Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions.
-Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.
-
-\subsubsection{smart contract}
-
-\subsubsection{IPFS}
-
-\subsubsection{MAM}
-
-\subsubsection{TangleID}
-
-\subsubsection{blind signature}
-
 \section{Trading Model}

### 2019-08-27 paper.tex

@@
 \subsubsection{Registrar}
-Registrar is responsible for creating a Registration Contract, which preserves a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
+Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
 
@@
 Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect raw data with their sensors and send it to the broker who will assist in uploading it to the network.
-A MAM channel\cite{MAM} is used to store  encrypted data stream.
+Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network.
+An MAM channel\cite{MAM} is used to store encrypted data stream.
 

### 2019-08-27 paper.tex
Add Component - TangleID

--- 2019-08-27 paper.tex
@@
 \subsubsection{TangleID}
+TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint.
+In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
+Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication.
+With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
 

### 2019-08-27 paper.tex
Add Component - IPFS

@@
 \subsubsection{IPFS}
+Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
+In our proposed architecture, brokers are responsible to upload the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
 

### 2019-08-27 paper.tex
Add Component - blind signature

@@
 
-\subsubsection{blind signature}
+\subsubsection{Blind Signature}
+Blind signature\cite{blindSig} is a form of digital signature where the message is blinded before it is signed, and the resulting blind signature can be verified publicly against the original.
+To perform such a signature, the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
+The resulting message, along with the blinding factor, can be later verified with the signer's public key.
+In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it.
+Furthermore, only one blind-signatured secret key is valid for trading and it is not allowed to be updated.
+By putting the secret key on smart contract prevents malicious providers trades invalid secret keys to consumers privately.
 

### 2019-08-28 paper.tex
Fix my email

--- 2019-08-27 paper.tex
@@
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv.tw@gmail.com, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
 }
@@
 
-\subsection{Component}
-\subsubsection{IOTA}
-IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
-To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions.
-Since every actor in Tangle has the same role, there is no need to offer transaction fees.
-Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions.
-Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.
-
-\subsubsection{smart contract}
-Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
-The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and with enforcement.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
-
-\subsubsection{IPFS}
-
-\subsubsection{Masked Authenticated Messaging}
-MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network.
-The consensus algorithm of IOTA ensures data integrity.
-These properties allow MAM to meet the requirements of both data integrity and privacy.
-
-IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used.
-However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only.
-Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private.
-In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.
-
-\subsubsection{TangleID}
-TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
-Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication.
-With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
-
-\subsubsection{blind signature}
-
 \section{Trading Model}

### 2019-08-28 paper.tex
Add Participants Registration and Launching and Searching Products

@@
 \usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage{amsmath}
 
@@
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv.tw@gmail.com, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
 }
@@
 \section{Trading Model}
+In the following, we describe the data trading process in detail.
+To participate a data marketplace, data providers and consumers have to register first.
+Then data provider can launch its product on the marketplace.
+Once a product is launched, it is searchable and could be traded afterward.
+The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
+
+\subsection{Participants Registration}
+At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
+Then some preselected brokers who are trustworthy are added to the decentralized data marketplace.
+Anyone who would like to sell or purchase data may register to become the data providers or consumers.
+The registrar has the authority to agree with applications.
+
+\subsection{Launching and Searching Products}
+To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
+
+Brokers certify session keys as well.
+However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
+Therefore, Blind signature is used to prevent the situation.
+When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded.
+Then the data provider sends the blinded session key to the broker.
+The broker signs the message and returns the signature to data provider.
+The data provider removes the blinding factor and obtains the broker's signature of the session key.
+Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
+
+The contract address and product description will be stored in a file which is uploaded to IPFS.
+Consumers can search the desired product by keywords or tags.
+The consumer then evaluates the product and start trading with the data provider if the consumer is interested in subscribing the data.
 

### 2019-08-28 paper.tex
Reword and add citations

--- 2019-08-27 paper.tex
@@
 
-\subsubsection{smart contract}
+\subsubsection{Ethereum Smart Contract}
 Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
@@
 TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
+In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
 Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication.

### 2019-08-28 paper.tex
Add Trading and Refunding

--- 2019-08-28 paper.tex
@@
 
+\subsection{Trading}
+Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers.
+The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
+After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts.
+For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
+Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
+Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸
+
+\subsection{Refunding}
+It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee.
+To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
+If the expected data is not available, subscribers can ask for refunds.
+We assume that less than half of subscribers in the Product Contract are irrational and malicious.
+Each subscriber can vote for refunding at any time.
+If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber.
+The subscription fee can be prorated as below:
+
+\begin{equation*}
+F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
+\end{equation*}
+
+\begin{equation*}
+F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
+\end{equation*}
+
+\begin{equation*}
+F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
+\end{equation*}
+
+Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.
+
 \section{Conclusion}

### 2019-08-28 paper.tex
Edit equation syntax

--- 2019-08-28 paper.tex
@@
 \section{Trading Model}
+In the following, we describe the data trading process in detail.
+To participate a data marketplace, data providers and consumers have to register first.
+Then data provider can launch its product on the marketplace.
+Once a product is launched, it is searchable and could be traded afterward.
+The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
+
+\subsection{Participants Registration}
+At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
+Then some preselected brokers who are trustworthy are added to the decentralized data marketplace.
+Anyone who would like to sell or purchase data may register to become the data providers or consumers.
+The registrar has the authority to agree with applications.
+
+\subsection{Launching and Searching Products}
+To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
+
+Brokers certify session keys as well.
+However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
+Therefore, Blind signature is used to prevent the situation.
+When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded.
+Then the data provider sends the blinded session key to the broker.
+The broker signs the message and returns the signature to data provider.
+The data provider removes the blinding factor and obtains the broker's signature of the session key.
+Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
+
+The contract address and product description will be stored in a file which is uploaded to IPFS.
+Consumers can search the desired product by keywords or tags.
+The consumer then evaluates the product and start trading with the data provider if the consumer is interested in subscribing the data.
+
+\subsection{Trading}
+Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers.
+The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
+After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts.
+For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
+Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
+Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸
+
+\subsection{Refunding}
+It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee.
+To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
+If the expected data is not available, subscribers can ask for refunds.
+We assume that less than half of subscribers in the Product Contract are irrational and malicious.
+Each subscriber can vote for refunding at any time.
+If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber.
+The subscription fee can be prorated as below:
+
+\begin{equation}
+F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
+\end{equation}
+
+\begin{equation}
+F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
+\end{equation}
+
+\begin{equation}
+F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
+\end{equation}
+
+Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.
 

### 2019-08-28 paper.tex
Add an author

@@
 %%% Fill in name here
-\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}} \\
+\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\
 
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
 
 %%% Fill in address here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
 %%% Fill in city and country here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.)} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
 }

### 2019-08-28 paper.tex
Add sequence diagrams of session key certification and exchange
Edit Trading Model

@@
 \usepackage{amsmath}
+\graphicspath{ {./images/} }
 
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{key_certification}
+	\caption{Session key certification with blind signature}
+	\label{fig:key_certification}
+\end{figure}
+
 The contract address and product description will be stored in a file which is uploaded to IPFS.
@@
 Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers.
 The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
@@
 For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
-Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
-Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸
+Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
+Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{key_exchange}
+	\caption{Session key exchange between the data provider and consumer}
+	\label{fig:key_exchange}
+\end{figure}
 
 \subsection{Refunding}
-It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee.
-To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
-If the expected data is not available, subscribers can ask for refunds.
-We assume that less than half of subscribers in the Product Contract are irrational and malicious.
+It is probable that the sensor is malfunctioning after the consumers pay the subscription fee.
+To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
+If the expected data is not available, consumers can ask for refunds.
+We assume that less than half of consumers in the Product Contract are irrational and malicious.
 Each subscriber can vote for refunding at any time.

### 2019-08-28 paper.tex
Add Game Theory Description

@@
 %%% Fill in name here
-\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\
+\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
 
@@
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
 }
@@
 
+The authors want to ensure the sustainability of decentralized data marketplace.
+The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}.
+Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy.
+data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
+
 Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers.
@@
 \subsection{Participants}
-There are four major roles in the decentralized data marketplace.
+There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).
 
@@
 After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{system_design}
+	\caption{System Design.}
+	\label{fig:system_design}
+\end{figure}
 
@@
 
+In our game theory model there are two kinds of players.
+One is data provider, and the other one is data buyer.
+Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
+The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough correct rate, $\pi_{correct}$.
+We deonte this correct rate threshold with $\pi_{threshold}$.
+Once the correct rate is lower than $\pi_{threshold}$, the data buyers would consider this data provider as a malicious data provider, and reject to buy the data from this data provider.
+
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
-Then some preselected brokers who are trustworthy are added to the decentralized data marketplace.
+At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
 Anyone who would like to sell or purchase data may register to become the data providers or consumers.
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{registration_contract}
+	\caption{Registration Contract.}
+	\label{fig:registration_contract}
+\end{figure}
+
 \subsection{Launching and Searching Products}
 To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{product_contract}
+\caption{Product Contract.}
+\label{fig:product_contract}
+\end{figure}
 
@@
 Therefore, Blind signature is used to prevent the situation.
-When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded.
+Figure \ref{fig:key_certification} shows the certification process.
+When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
 Then the data provider sends the blinded session key to the broker.
@@
 	\includegraphics[width=0.5\textwidth]{key_certification}
-	\caption{Session key certification with blind signature}
+	\caption{Session key certification process with blind signature.}
 	\label{fig:key_certification}
@@
 \subsection{Trading}
-Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers.
-The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
-After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts.
-For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
+Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
+After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract.
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
-Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸
+Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
 
@@
 	\includegraphics[width=0.5\textwidth]{key_exchange}
-	\caption{Session key exchange between the data provider and consumer}
+	\caption{Session key exchange process between the data provider and consumer.}
 	\label{fig:key_exchange}
@@
 We assume that less than half of consumers in the Product Contract are irrational and malicious.
-Each subscriber can vote for refunding at any time.
-If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber.
+Each consumer can vote for refunding at any time.
+If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
 The subscription fee can be prorated as below:
@@
 
-Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.
+where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of consumers in this contract.
+
+To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee.
+We assume that only a half of the expected records are uploaded to the MAM channel.
+For the data provider and broker, they can withdraw a half of total subscription fee from the smart contract and $F_{b}$ \% belongs to the broker while the remaining belongs to the data provider.
+For consumers, they can get a half refund which should be deducted the transaction fee.
+
+\subsection{Game Theory Evaluation}
+
+\subsubsection{Model Description}
+Repeated game consists of serveral repetitions of some stage games.
+In each stage game, the action player takes will effect the actions that players are going to take in the future stages.
+Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff.
+Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.
+
+We use a repeated game to express the scenario of our Data Marketplace.
+Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
+Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay $p_{fee}$ in total to buy the data.
+
+\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
+    \label{fig:decision_tree} \end{figure}
+For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns.
+We call this as a maintain period.
+Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.
+
+We have these following assumptions:
+\begin{itemize}
+\item  There is no any other data providers provide the same product in Data Marketplace.
+Therefore, we can consider each provider's behavior independently.
+That means this decision tree represent the behavior of only one data provider.
+\item  More than 51\% of data buyers are amoung complete information exchange state.
+In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
+\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out the wrong or fake data provided by data provider is wrong.
+\end{itemize}
+
+Based on the description above, the discount sum of payoff for our repeated game is 
+\begin{equation} \label{payoff}
+\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot p_{fee}) - C_{maintain}]}
+\end{equation}
+
+Al-Fagih et al.
+presented\cite{DataPrice} $p_{fee}$ is a sigmoid function of $\pi_{correct}$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $\pi_{correct}$.
+We can substitute $p_{fee}$ and $C_{maintain}$ with $\pi_{correct}$ into Eq.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game with differential easily.
 

### 2019-08-28 paper.tex
Edit Trading Model

--- 2019-08-28 paper.tex
@@
 Therefore, Blind signature is used to prevent the situation.
+Figure \ref{fig:key_certification} shows the certification process.
 When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded.
@@
 \subsection{Trading}
-Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers.
-The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
-After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts.
-For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
+Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
+After that, the data provider can also get public keys of each consumer from the Registration Contact with their accounts.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract.
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
@@
 
-Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.
+where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of consumers in this contract.
+
+To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee.
+We assume that only a half of the expected records are uploaded to the MAM channel.
+For the data provider and broker, they can withdraw a half of total subscription fee from the smart contract and $F_{b}$ \% belongs to the broker while the remaining belongs to the data provider.
+For consumers, they can get a half refund which should be deducted the transaction fee.
 

### 2019-08-28 paper.tex
Reorder author list

--- 2019-08-28 paper.tex
@@
 \usepackage{amsmath}
-\graphicspath{ {./images/} }
 
@@
 %%% Fill in name here
-\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\
+\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{key_certification}
-	\caption{Session key certification with blind signature}
-	\label{fig:key_certification}
-\end{figure}
-
 The contract address and product description will be stored in a file which is uploaded to IPFS.
@@
 Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers.
+To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers.
 The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber.
@@
 For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
-Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{key_exchange}
-	\caption{Session key exchange between the data provider and consumer}
-	\label{fig:key_exchange}
-\end{figure}
+Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
+Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸
 
 \subsection{Refunding}
-It is probable that the sensor is malfunctioning after the consumers pay the subscription fee.
-To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
-If the expected data is not available, consumers can ask for refunds.
-We assume that less than half of consumers in the Product Contract are irrational and malicious.
+It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee.
+To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
+If the expected data is not available, subscribers can ask for refunds.
+We assume that less than half of subscribers in the Product Contract are irrational and malicious.
 Each subscriber can vote for refunding at any time.

### 2019-08-28 paper.tex
Add diagrams of smart contracts

--- 2019-08-28 paper.tex
@@
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
+At the beginning, the registrar creates a Registration Contact (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
 Then some preselected brokers who are trustworthy are added to the decentralized data marketplace.

### 2019-08-29 paper.tex
Edit Trading Model

@@
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contact (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys.
-Then some preselected brokers who are trustworthy are added to the decentralized data marketplace.
+At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
 Anyone who would like to sell or purchase data may register to become the data providers or consumers.
@@
 Figure \ref{fig:key_certification} shows the certification process.
-When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded.
+When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
 Then the data provider sends the blinded session key to the broker.
@@
 The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
-After that, the data provider can also get public keys of each consumer from the Registration Contact with their accounts.
+After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
 For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract.
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
-Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸
+Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
 

### 2019-08-29 paper.tex
Fix denotation

@@
 %%% Fill in name here
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
 
@@
 However, there are some potential threats need to be resolved, such as payment fairness, authentication of the participants, faithful delivery of data and probable malicious behaviour of data marketplace participants.
+
+The authors want to ensure the sustainability of decentralized data marketplace.
+The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}.
+Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy.
+data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
 
@@
 The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
+
+In our game theory model there are two kinds of players.
+One is data provider, and the other one is data buyer.
+Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
+The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough correct rate, $P_r$. We deonte this correct rate threshold with $\xi$.
+Once the correct rate is lower than $\xi$, the data buyers would consider this data provider as a malicious data provider, and reject to buy the data from this data provider.
 
@@
 
+\subsection{Game Theory Evaluation}
+
+\subsubsection{Model Description}
+Repeated game consists of serveral repetitions of some stage games.
+In each stage game, the action player takes will effect the actions that players are going to take in the future stages.
+Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff.
+Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.
+
+We use a repeated game to express the scenario of our Data Marketplace.
+Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
+Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $P_s$, in total to buy the data.
+
+\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
+    \label{fig:decision_tree} \end{figure}
+For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns.
+We call this as a maintain period.
+Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.
+
+We have these following assumptions:
+\begin{itemize}
+\item  There is no any other data providers provide the same product in Data Marketplace.
+Therefore, we can consider each provider's behavior independently.
+That means this decision tree represent the behavior of only one data provider.
+\item  More than 51\% of data buyers are among complete information exchange state.
+In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
+\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out the wrong or fake data provided by data provider is wrong.
+\end{itemize}
+
+Based on the description above, the discount sum of payoff for our repeated game is 
+\begin{equation} \label{payoff}
+\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
+\end{equation}
+
+\begin{itemize}
+\item $P_s$ is the sum of subscription price (fee) for all subscriber.
+\item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
+\item $\beta$ is discounted factor.
+\item $n$ is how many round for one maintenance period.
+\item $m$ is how many maintenance periods have been experienced in this repeated game.
+\end{itemize}
+
+Al-Fagih et al.
+presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
+We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game with differential easily.
+
 \section{Conclusion}

### 2019-08-29 paper.tex
Add game theory description for refund

@@
 Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
-The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough correct rate, $P_r$. We deonte this correct rate threshold with $\xi$.
-Once the correct rate is lower than $\xi$, the data buyers would consider this data provider as a malicious data provider, and reject to buy the data from this data provider.
+The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, $P_r$. We deonte this accuracy threshold with $\xi$.
+Once the accuracy is lower than $\xi$, the data buyers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
 
@@
 
-\subsubsection{Model Description}
 Repeated game consists of serveral repetitions of some stage games.
@@
 Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $P_s$, in total to buy the data.
+
+Refund is a major issue in our research.
+However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
+The subscription fee will be paid as data provider provides new data.
+In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to data buyers' account.
+For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
 
@@
 In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out the wrong or fake data provided by data provider is wrong.
+\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out if wrong data or low accuracy data are delivered to data buyers.
 \end{itemize}
@@
 We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
-(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game with differential easily.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.
 

### 2019-08-30 paper.tex
Edit Trading Model

--- 2019-08-29 paper.tex
@@
 %%% Fill in name here
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\
 
@@
 \subsection{Participants}
-There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).
+There are four major roles in the decentralized data marketplace.
 
@@
 Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power.
-Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to the IPFS (InterPlanetary File System)\cite{IPFS}.
+Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}.
 Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption.
@@
 After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{system_design}
-	\caption{System Design.}
-	\label{fig:system_design}
-\end{figure}
 
@@
 The registrar has the authority to agree with applications.
+After that, their identities are available in the Registration Contract and launching and trading processes can be started.
 
@@
 Brokers certify session keys as well.
+Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
 However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
@@
 Figure \ref{fig:key_certification} shows the certification process.
-When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
-Then the data provider sends the blinded session key to the broker.
-The broker signs the message and returns the signature to data provider.
-The data provider removes the blinding factor and obtains the broker's signature of the session key.
-Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
+When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
+Then the data provider sends the blinded session key $Blind(k)$ to the broker.
+The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider.
+The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.
 
@@
 Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
 The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
 After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
-For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
+Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
 Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.

### 2019-08-30 paper.tex
Edit Trading Model
Modify related work

--- 2019-08-29 paper.tex
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
 
@@
 \section{Related Work}
-The increasing IoT devices brings a huge amount of data, the economic value becomes essential for parties intended to sell, buy and find data.
-The need for IoT data marketplace arises due to this.
-Recent years, several researchers has started to explore based on this concept.
-There are some critical issues need to be resolved in the design of data marketplace platform, in this paper, we focus on two issues, data integrity and the trading behavior.
+The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
+The Third Party Auditors (TPAs)-based frameworks is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data.
+Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.
 
-To ensure data integrity for IoT applications is always a challenge because of the unstandardize data format and dynamic nature.
-Moreover, the Third Party Auditors (TPAs)-based frameworks is far from being satisfactory.
-Therefore a decentralized data integrity validation has been proposed recent years, and blockchain is considered a solution.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract and Cloud Server.
+Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization.
+However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers.
+Also, the performance analysis shows that IoT devices have low efficiency interacting with Etheruem due to the time-consuming Proof-of-Work(PoW) process.
 
-Data Integrity as a Service (DIaas) is a blockchain based framework for data integrity proposed by Bin Liu\cite{DIaas}.
-DIaas is a Cloud Server Service (CSS) for IoT dynamic data that allows both data owner and data consumer to validate data integrity by comparing hashes on smart contract  and on Cloud Server.
-Besides, smart contract can also realize the purchase agreement, including authorizing data consumer for specific data set and even the penalty for data provider if they fail to provide the data integrity.
-However, the performance analysis shows that IoT devices still have low efficiency interacting with Etheruem, this may fall to the Proof-of-Work (PoW) process is time-consuming for an IoT device and the blockchain consensus can not be reached within a short time, while Ethereum is expected to enable consensus within 12-second but the time is still longer when the authors wrote the paper.
+By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
+On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit and access an encrypted data stream over the Tangle where privacy and integrity meet.
 
-By solving the inefficiencies of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry or Web 3.0 based on the revolutionary distributed ledger technology, the \textbf{Tangle}.
-It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public.
-On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM.
-But only the data buyout doesn't meet the need of the real world, such as data subscription and a specific time period of data maybe needed for different uses.
-Moreover, even though IOTA needs less computing power than other blockchain system, doing PoW and unstable network environment are still the bottleneck for low-level devices, it may take 2 or more minutes to issue a transaction to Tangle under MAM protocol.
+On the basis of the Tangle and MAM, IOTA foundation proposed a decentralized Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM.
+Nevertheless, the platform design is centralized, new devices require manual approval from IOTA team to be visible in the marketplace.
+Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.
 
-A different framework design proposed by Pooja Gupta, Salil S.Kanhere and Raja Jurdak\cite{3tierDataMarket} could solve the efficiency problem as mentioned.
-The infrastructure is a 3-tier decentralized data marketplace architectural design with smart contract which consists of provider, consumer and broker.
+A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned.
+The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker.
 Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers.
-However, there are some potential threats need to be resolved, such as payment fairness, authentication of the participants, faithful delivery of data and probable malicious behaviour of data marketplace participants.
+However, the data integrity and authentication of each participant are still future work.
 
@@
 
-Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers.
-In our infrastructure, the identity of each participants could be easily verified with a self-soverign identity system, also we design the refunding mechanism to protect the payment fairness.
-Moreover, with MAM as our data storage on IOTA, data could be delivered securely and faithfully without any third-parties.
+The previous work proposed different solution to specific issues of data marketplace.
+In this paper, we proposed an  overall design of decentralized data markeplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.
 
 \section{System Architecture}
+Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
+
 \subsection{Participants}
@@
 \subsection{Game Theory Evaluation}
-
+\subsubsection{Repeated Game}
 Repeated game consists of serveral repetitions of some stage games.
@@
 
+\subsubsection{Model Description}
 We use a repeated game to express the scenario of our Data Marketplace.
 Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
-Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $P_s$, in total to buy the data.
+Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $p_s$, each person.
+The sum of all the subscription fee pays to data provider is denoted as $P_s$.
 
@@
 We call this as a maintain period.
-Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.
+Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.
 
@@
 In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out if wrong data or low accuracy data are delivered to data buyers.
+\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
+If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
 \end{itemize}
 
-Based on the description above, the discount sum of payoff for our repeated game is 
+Based on the description above, the discounted sum of payoff for our repeated game is 
 \begin{equation} \label{payoff}

### 2019-08-30 paper.tex
Add numerical analysis

--- 2019-08-30 paper.tex
@@
-\documentclass[journal,a4paper]{IEEEtran}
+\documentclass[journal,10pt,a4paper]{IEEEtran}
 
-% to typeset URLs, URIs, and DOIs
 \usepackage[english]{babel}
@@
 \begin{document}
-%
-\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
-%
+\title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
 \author{
-%%% Fill in name here
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+    \large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua (Vivian) Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}
 
-%%% Fill in school here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
 
-%%% Fill in address here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
-%%% Fill in city and country here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
-%%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
+    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
 }
 
-%
+\maketitle
+\section{\normalsize\textbf{Abstract}}
+Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
+But IoT cannot be considered a mere extension of DaaS.
+Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability.
+Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
 
-\maketitle              
-% 50-80 words
-\begin{abstract}
-abstract here
-\end{abstract}
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers.
+This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform.
+Later, the verified data will enter data marketplace to be traded.
+Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
 
-% 3 - 4 keywords
 \begin{IEEEkeywords}
@@
 
-\section{Introduction}
+\section{\normalsize\textbf{Introduction}}
+The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
+As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
+This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems.
+Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
+We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
+\begin{enumerate}
+    \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
+    \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
+    \item Data owners do not know how to discover knowledge from raw data.
+\end{enumerate}
 
-\section{Related Work}
+To overcome these barriers, we implement IoT-enabled Data Marketplace and sensor data submission functionalities are intended to be very lightweight, capable of running on embedded devices.
+They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
+This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
+\begin{enumerate}
+    \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
+    \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
+    \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
+\end{enumerate}
+
+Take the use case of Airbox\cite{LASS} for instance.
+Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
+To protect privacy, data should be encrypted before on-chain.
+As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction.
+At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
+Last but not least, payments will be stored on the smart contracts until the transactions are confirmed.
+The whole sequence is illustrated in Figure \ref{fig:airbox}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{airbox}
+    \caption{IoT-enabled personal air quality assistant.}
+    \label{fig:airbox}
+\end{figure}
+
+\section{\normalsize\textbf{Related Work}}
 The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
@@
 
-The authors want to ensure the sustainability of decentralized data marketplace.
-The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}.
+The utility structure of IoT econimic system and game theory models are evaluated by Dusit Niyato et al.\cite{UtilityStruct}.
 Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy.
-data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
+The authors ensures the sustainability of IoT economy by game theory.
+Data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
+However, few things didn't be mentioned in their work including refund and subscription economy.
 
@@
 
-\section{System Architecture}
-Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
+\section{\normalsize\textbf{System Architecture}}
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
 
@@
 \subsubsection{Data Provider}
-Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers.
+Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers.
 They decide the subscription period, subscription price, data type, sampling frequency.
 Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network.
+Next, they collect raw data and send to the broker who assists in uploading data to the network.
 An MAM channel\cite{MAM} is used to store encrypted data stream.
+They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
 
 \subsubsection{Consumer}
-Consumers aspire to obtain IoT data to promote the value of their service.
+Consumers aspire to obtain streaming data to promote the value of their service.
 However, it is a big challenge for most consumers to collect the desired data by themselves.
-So they look forward to purchasing the IoT data from data providers.
+So they look forward to purchasing the streaming data from data providers.
+They search products on the marketplace and pay for subscription fee.
+While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically.
+The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains streaming data.
 
@@
 After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+For each products, brokerage fees will be charged by the broker.
 
@@
 \subsection{Component}
-\subsubsection{IOTA}
-IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
-To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions.
-Since every actor in Tangle has the same role, there is no need to offer transaction fees.
-Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions.
-Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.
+\subsubsection{Masked Authenticated Messaging}
+IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
+The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions.
+Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.
+
+However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
+It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel.
+Furthermore, a session key can be provided to control the visibility and access to a MAM channel.
+
+\subsubsection{TangleID}
+TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
+In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
+With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.
 
@@
 
+\subsubsection{Blind Signature}
+Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
+The resulting message, along with the blinding factor, can be later verified with the signer's public key.
+In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it.
+
 \subsubsection{IPFS}
@@
 
-\subsubsection{Masked Authenticated Messaging}
-MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network.
-The consensus algorithm of IOTA ensures data integrity.
-These properties allow MAM to meet the requirements of both data integrity and privacy.
-
-IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used.
-However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only.
-Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private.
-In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.
-
-\subsubsection{TangleID}
-TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
-Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication.
-With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
-
-\subsubsection{Blind Signature}
-Blind signature\cite{blindSig} is a form of digital signature where the message is blinded before it is signed, and the resulting blind signature can be verified publicly against the original.
-To perform such a signature, the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it.
-Furthermore, only one blind-signatured secret key is valid for trading and it is not allowed to be updated.
-By putting the secret key on smart contract prevents malicious providers trades invalid secret keys to consumers privately.
-
-\section{Trading Model}
+\section{\normalsize\textbf{Trading Model}}
 In the following, we describe the data trading process in detail.
@@
 
-In our game theory model there are two kinds of players.
-One is data provider, and the other one is data buyer.
-Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
-The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, $P_r$. We deonte this accuracy threshold with $\xi$.
-Once the accuracy is lower than $\xi$, the data buyers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
+Data provider would receive subscription fee for buying data each time the data is transmitted to consumer; unpaid subscription fee would be stored in smart contract.
+The consumer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, which we called these data as decent data.
+Once the accuracy is lower than a certain accuracy, which we called it as unacceptable data, the consumers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
 
@@
 At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+Only one Registration Contract is needed, and everyone can query the participants' public keys.
 Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
@@
 \subsection{Launching and Searching Products}
-To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}
 
@@
 
+To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
+Each product has a Product Contract to record the trading process.
+
 Brokers certify session keys as well.
+Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
 However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
@@
 \subsection{Trading}
-Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
-The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
-After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
-For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature.
-Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{trading_product}
+    \caption{The process of the product trading.}
+    \label{fig:trading_product}
+\end{figure}
 
@@
 
+The whole trading process is shown in Figure \ref{fig:trading_product}.
+Once a consumer who want to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
+To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+
+The data provider requests the consumers list maintained by the Product Contract and obtains accounts of each consumer.
+After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
+Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
+
+Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Afterward, encrypted data is uploaded to the MAM channel, and consumers can download and decrypt it with the session key.
+
 \subsection{Refunding}
-It is probable that the sensor is malfunctioning after the consumers pay the subscription fee.
+It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee.
 To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
@@
 Each consumer can vote for refunding at any time.
-If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
+If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
 The subscription fee can be prorated as below:
@@
 \begin{equation}
-F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
+    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) (1-F_{t})
 \end{equation}
@@
 \begin{equation}
-F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
+    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} (1-F_{t})
 \end{equation}
@@
 \begin{equation}
-F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
+    F_{Consumer}(i) = price \frac{M-i+1}{M} (1-F_{t})
 \end{equation}
@@
 Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
-Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $p_s$, each person.
+Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person.
 The sum of all the subscription fee pays to data provider is denoted as $P_s$.
@@
 The subscription fee will be paid as data provider provides new data.
-In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to data buyers' account.
+In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to consumers' account.
 For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
 
-\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
+\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
     \label{fig:decision_tree} \end{figure}
@@
 That means this decision tree represent the behavior of only one data provider.
-\item  More than 51\% of data buyers are among complete information exchange state.
+    \item  More than 51\% of consumers are among complete information exchange state.
 In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
-If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
+    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
+If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
 \end{itemize}
@@
 \begin{equation} \label{payoff}
-\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
+    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
 \end{equation}
@@
 Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
+presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
 We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
-(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.
+We will discuss more in the next section.
 
-\section{Conclusion}
+\subsubsection{Numerical Example}
+To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as function of $P_r$ respectively.
+Therefore, the sum of subscription fee of all subscriber can be expressed as
+
+\begin{equation} \label{sub_fee}
+P_s = R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}
+\end{equation}
+
+where $a$ and $b$ are tuning factors, and $R$ is the maximun data value.
+And we would express the cost of maintenance as
+
+\begin{equation} \label{C_mtn}
+C_{maintain} = ce^{P_r - d}
+\end{equation}
+Where $c$ and $d$ is tuning factor.
+
+Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
+\begin{equation} \label{payoff_Pr}
+\sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
+\end{equation}
+
+Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and there is only one maintenance period has happened and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
+Based on these parameters, we can plot the payoff function as function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
+The maximun point occurs at $accuracy \approx 92\%$ which we point it out with red dot.
+\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
+    \label{fig:payoff_pic} \end{figure}
+
+Figure.\ref{fig:payoff_pic} illustratres the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is mush less than moderate quality data.
+Second the great deficit at high accuracy is mostly drived by the rapid increasing of maintenance cost.
+Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
+
+\section{\normalsize\textbf{Conclusion}}
 
@@
 \bibliography{references}
-
 \end{document}

### 2019-08-30 paper.tex
Revise equations

--- 2019-08-30 paper.tex
@@
 %%% Fill in name here
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\
 
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
 
@@
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
 }
@@
 
-The authors want to ensure the sustainability of decentralized data marketplace.
-The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}.
-Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy.
-data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
-
 Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers.
@@
 
-In our game theory model there are two kinds of players.
-One is data provider, and the other one is data buyer.
-Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
-The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, $P_r$. We deonte this accuracy threshold with $\xi$.
-Once the accuracy is lower than $\xi$, the data buyers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
-
 \subsection{Participants Registration}
 At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+Only one Registration Contract is needed, and everyone can query the participants' public keys.
 Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
@@
 The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
+Each product has a Product Contract to record the trading process.
 
@@
 Each consumer can vote for refunding at any time.
-If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
+If the ratio of consent votes of refunding is higher than the $threshold$ at $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
 The subscription fee can be prorated as below:
@@
 \begin{equation}
-F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
+F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) (1-F_{t})
 \end{equation}
@@
 \begin{equation}
-F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
+F_{Broker}(i) = N price \frac{i-1}{M} F_{b} (1-F_{t})
 \end{equation}
@@
 \begin{equation}
-F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
+F_{Consumer}(i) = price \frac{M-i+1}{M} (1-F_{t})
 \end{equation}
@@
 
-\subsection{Game Theory Evaluation}
-\subsubsection{Repeated Game}
-Repeated game consists of serveral repetitions of some stage games.
-In each stage game, the action player takes will effect the actions that players are going to take in the future stages.
-Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff.
-Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.
-
-\subsubsection{Model Description}
-We use a repeated game to express the scenario of our Data Marketplace.
-Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
-Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $p_s$, each person.
-The sum of all the subscription fee pays to data provider is denoted as $P_s$.
-
-Refund is a major issue in our research.
-However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
-The subscription fee will be paid as data provider provides new data.
-In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to data buyers' account.
-For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
-
-\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
-    \label{fig:decision_tree} \end{figure}
-For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns.
-We call this as a maintain period.
-Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.
-
-We have these following assumptions:
-\begin{itemize}
-\item  There is no any other data providers provide the same product in Data Marketplace.
-Therefore, we can consider each provider's behavior independently.
-That means this decision tree represent the behavior of only one data provider.
-\item  More than 51\% of data buyers are among complete information exchange state.
-In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
-If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
-\end{itemize}
-
-Based on the description above, the discounted sum of payoff for our repeated game is 
-\begin{equation} \label{payoff}
-\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
-\end{equation}
-
-\begin{itemize}
-\item $P_s$ is the sum of subscription price (fee) for all subscriber.
-\item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
-\item $\beta$ is discounted factor.
-\item $n$ is how many round for one maintenance period.
-\item $m$ is how many maintenance periods have been experienced in this repeated game.
-\end{itemize}
-
-Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
-We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
-(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.
-
 \section{Conclusion}

### 2019-08-30 paper.tex
Minor style tweak

--- 2019-08-30 paper.tex
@@
 %%% Fill in school here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
+\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
 \IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

### 2019-08-30 paper.tex
Modify Component

@@
 \section{System Architecture}
-Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
 
@@
 \subsection{Component}
-\subsubsection{IOTA}
-IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
-To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions.
-Since every actor in Tangle has the same role, there is no need to offer transaction fees.
-Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions.
-Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.
+\subsubsection{Masked Authenticated Messaging}
+IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
+The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions.
+Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.
+
+However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity. 
+It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel.
+Furthermore, a session key can be provided to control the visibility and access to a MAM channel.
+
+\subsubsection{TangleID}
+TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
+In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
+With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.
 
@@
 In our proposed architecture, brokers are responsible to upload the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
-
-\subsubsection{Masked Authenticated Messaging}
-MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network.
-The consensus algorithm of IOTA ensures data integrity.
-These properties allow MAM to meet the requirements of both data integrity and privacy.
-
-IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used.
-However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only.
-Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private.
-In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.
-
-\subsubsection{TangleID}
-TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
-Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication.
-With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
-
-\subsubsection{Blind Signature}
-Blind signature\cite{blindSig} is a form of digital signature where the message is blinded before it is signed, and the resulting blind signature can be verified publicly against the original.
-To perform such a signature, the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it.
-Furthermore, only one blind-signatured secret key is valid for trading and it is not allowed to be updated.
-By putting the secret key on smart contract prevents malicious providers trades invalid secret keys to consumers privately.
 

### 2019-08-30 paper.tex
Edit Participants and Trading Model

@@
 An MAM channel\cite{MAM} is used to store encrypted data stream.
+They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their sensors.
 
@@
 So they look forward to purchasing the IoT data from data providers.
+They search products on the marketplace and pay for subscription fee.
+While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically.
+The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains sensing data.
 
@@
 \subsection{Trading}
-Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract.
+Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
 To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
-The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer.
+
+The data provider requests the consumers list maintained by the Product Contract and obtains accounts of each consumer.
 After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
@@
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
+
 Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
@@
 Each consumer can vote for refunding at any time.
-If the ratio of consent votes of refunding is higher than the $threshold$ at $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
+If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
 The subscription fee can be prorated as below:

### 2019-08-30 paper.tex
Add diagrams of product launching and trading

@@
 \subsection{Launching and Searching Products}
-To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
-Each product has a Product Contract to record the trading process.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{launching_product}
+	\caption{The process of launching a product.}
+	\label{fig:launching_product}
+\end{figure}
 
@@
 \end{figure}
+
+To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
+Each product has a Product Contract to record the trading process.
 
@@
 \subsection{Trading}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{trading_product}
+	\caption{The process of the product trading.}
+	\label{fig:trading_product}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{key_exchange}
+	\caption{Session key exchange process between the data provider and consumer.}
+	\label{fig:key_exchange}
+\end{figure}
+
+The whole trading process is shown in Figure \ref{fig:trading_product}.
 Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
@@
 Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{key_exchange}
-	\caption{Session key exchange process between the data provider and consumer.}
-	\label{fig:key_exchange}
-\end{figure}
 

### 2019-08-30 paper.tex
Modify 'sensor' to 'streaming data sources'

@@
 \section{System Architecture}
-Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
+Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.
 
@@
 \subsubsection{Data Provider}
-Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers.
+Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers.
 They decide the subscription period, subscription price, data type, sampling frequency.
 Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network.
+Next, they collect raw data and send to the broker who assists in uploading data to the network.
 An MAM channel\cite{MAM} is used to store encrypted data stream.
-They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their sensors.
+They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
 
 \subsubsection{Consumer}
-Consumers aspire to obtain IoT data to promote the value of their service.
+Consumers aspire to obtain streaming data to promote the value of their service.
 However, it is a big challenge for most consumers to collect the desired data by themselves.
-So they look forward to purchasing the IoT data from data providers.
+So they look forward to purchasing the streaming data from data providers.
 They search products on the marketplace and pay for subscription fee.
 While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically.
-The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains sensing data.
+The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains streaming data.
 
@@
 
-To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
 The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
@@
 The whole trading process is shown in Figure \ref{fig:trading_product}.
-Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
+Once a consumer who want to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
 To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
@@
 Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
+Afterward, encrypted data is uploaded to the MAM channel, and consumers can download and decrypt it with the session key.
 
 \subsection{Refunding}
-It is probable that the sensor is malfunctioning after the consumers pay the subscription fee.
+It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee.
 To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.

### 2019-08-31 paper.tex

@@
 The subscription fee will be paid as data provider provides new data.
-In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to data buyers' account.
+In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to consumers' account.
 For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
@@
 That means this decision tree represent the behavior of only one data provider.
-\item  More than 51\% of data buyers are among complete information exchange state.
+\item  More than 51\% of consumers are among complete information exchange state.
 In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
-If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
+\item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
+If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
 \end{itemize}

### 2019-08-31 paper.tex

@@
 \section{System Architecture}
-Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.
 

### 2019-09-01 paper.tex
Style tweak

@@
 %
-\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
+\title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
 %
@@
 %%% Fill in name here
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+%\IEEEauthorblockN{
+\large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}
+%}\\
 
 %%% Fill in school here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
 
 %%% Fill in address here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
 %%% Fill in city and country here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
 %%% Fill in email here
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
 }
@@
 % 50-80 words
-\begin{abstract}
-abstract here
-\end{abstract}
+\section{\normalsize\textbf{Abstract}}
+Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
+But IoT cannot be considered a mere extension of DaaS.
+Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability.
+Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
 
-% 3 - 4 keywords
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers.
+This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform.
+Later, the verified data will enter data marketplace to be traded.
+Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
+
 \begin{IEEEkeywords}
@@
 
-\section{Introduction}
+\section{\normalsize\textbf{Introduction}}
+The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
+As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
+This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems.
+Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
+We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
+\begin{enumerate}
+  \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
+  \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
+  \item Data owners do not know how to discover knowledge from raw data.
+\end{enumerate}
 
-\section{Related Work}
+To overcome these barriers, we implement IoT-enabled Data Marketplace and sensor data submission functionalities are intended to be very lightweight, capable of running on embedded devices.
+They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
+This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
+\begin{enumerate}
+  \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
+  \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
+  \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
+\end{enumerate}
+
+Take the use case of Airbox\cite{LASS} for instance.
+Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
+To protect privacy, data should be encrypted before on-chain.
+As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction.
+At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
+Last but not least, payments will be stored on the smart contracts until the transactions are confirmed.
+The whole sequence is illustrated in Figure \ref{fig:airbox}.
+
+\begin{figure}[h]
+        \centering
+	\includegraphics[width=0.5\textwidth]{airbox}
+	\caption{IoT-enabled personal air quality assistant.}
+	\label{fig:airbox}
+\end{figure}
+
+\section{\normalsize\textbf{Related Work}}
 The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
@@
 
-\section{System Architecture}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.
+\section{\normalsize\textbf{System Architecture}}
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
 
@@
 
-\section{Trading Model}
+\section{\normalsize\textbf{Trading Model}}
 In the following, we describe the data trading process in detail.
@@
 
-\section{Conclusion}
+\section{\normalsize\textbf{Conclusion}}
 

### 2019-09-01 paper.tex
Add summary

--- 2019-08-31 paper.tex
@@
 \begin{abstract}
-abstract here
+Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and have come to form a multi-billion dollar industry.
+But IoT cannot be considered a mere extension of DaaS.
+Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability.
+Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
+
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers.
+This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform in claim of "being tradable." Later, the verified data will enter data marketplace to be traded.
+Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
 \end{abstract}

### 2019-09-01 paper.tex
Add introduction

@@
 This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
-In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform in claim of "being tradable." Later, the verified data will enter data marketplace to be traded.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform.
+Later, the verified data will enter data marketplace to be traded.
 Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
@@
 \section{Introduction}
+The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
+As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
+This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems.
+Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
+We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
+\begin{enumerate}
+  \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
+  \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
+  \item Data owners do not know how to discover knowledge from raw data.
+\end{enumerate}
+
+To overcome these barriers, we implement IoT-enabled Data Marketplace and sensor data submission functionalities are intended to be very lightweight, capable of running on embedded devices.
+They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
+This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
+\begin{enumerate}
+  \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
+  \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
+  \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
+\end{enumerate}
+
+Take the use case of Airbox\cite{LASS} for instance.
+Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
+To protect privacy, data should be encrypted before on-chain.
+As for the data reliability, BiiLabs designs the smart-contract-oriented structure to write down every transaction.
+At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
+Last but not least, payments will be stored on the smart contracts until the transactions are confirmed.
+The whole sequence is illustrated in Figure \ref{fig:airbox}.
+
+\begin{figure}[h]
+        \centering
+	\includegraphics[width=0.5\textwidth]{airbox}
+	\caption{IoT-enabled personal air quality assistant.}
+	\label{fig:airbox}
+\end{figure}
 

### 2019-09-01 paper.tex
Fix wording
Clean up
Fix wording on DaaS

@@
 
-% to typeset URLs, URIs, and DOIs
 \usepackage[english]{babel}
@@
 \begin{document}
-%
 \title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
-%
 \author{
-%%% Fill in name here
 \IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
 
-%%% Fill in school here
 \IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
@@
 
-%%% Fill in address here
 \IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
-%%% Fill in city and country here
 \IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
-%%% Fill in email here
 \IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
@@
 
-%
-
 \maketitle
-% 50-80 words
 \begin{abstract}
-Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and have come to form a multi-billion dollar industry.
+Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
 But IoT cannot be considered a mere extension of DaaS.
@@
 
-% 3 - 4 keywords
 \begin{IEEEkeywords}
@@
 To protect privacy, data should be encrypted before on-chain.
-As for the data reliability, BiiLabs designs the smart-contract-oriented structure to write down every transaction.
+As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction.
 At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.

### 2019-09-01 paper.tex
Cite Self-driving paper for digital twins

@@
 The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
-As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
+As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
 This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems.

### 2019-09-02 paper.tex
Modify my name

@@
-\documentclass[journal,a4paper]{IEEEtran}
+\documentclass[journal,10pt,a4paper]{IEEEtran}
 
@@
 \begin{document}
-\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
+%
+\title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
+%
 \author{
-\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\
+%%% Fill in name here
+%\IEEEauthorblockN{
+\large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua (Vivian) Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}
+%}\\
 
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
-\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
+%%% Fill in school here
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\
 
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
+%%% Fill in address here
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
-\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
+%%% Fill in city and country here
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
-\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
+%%% Fill in email here
+\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
 }
 
+%
+
 \maketitle              
-\begin{abstract}
+% 50-80 words
+\section{\normalsize\textbf{Abstract}}
 Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
@@
 Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
-\end{abstract}
 
@@
 
-\section{Introduction}
+\section{\normalsize\textbf{Introduction}}
 The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
@@
 
-\section{Related Work}
+\section{\normalsize\textbf{Related Work}}
 The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.

### 2019-09-07 paper.tex
Consolidate image collections
Minor clean up
Enforce latexindent
Add future work - data auction

@@
 \begin{document}
-%
 \title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
-%
 \author{
-%%% Fill in name here
-%\IEEEauthorblockN{
     \large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua (Vivian) Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}
-%}\\
 
-%%% Fill in school here
     \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
@@
 
-%%% Fill in address here
     \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\
 
-%%% Fill in city and country here
     \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\
 
-%%% Fill in email here
     \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
@@
 
-%
-
 \maketitle
-% 50-80 words
-\section{\normalsize\textbf{Abstract}}
+\section*{\normalsize\textbf{Abstract}}
 Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
@@
 
-\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
+\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
     \label{fig:decision_tree} \end{figure}
@@
 
-\section{\normalsize\textbf{Conclusion}}
+\section{\normalsize\textbf{Future Work}}
+%Data Auction
+The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers.
+While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform.
+Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers.
+However, the auction process between multiple participants and analyzing potential threats are still critical issues that need to be resolved.
 

### 2019-09-07 paper.tex
Modify Component - MAM

@@
 \section*{\normalsize\textbf{Abstract}}
-Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
+Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry.
 But IoT cannot be considered a mere extension of DaaS.
-Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability.
+Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability.
 Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
 
-In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers.
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers.
 This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
-In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform.
-Later, the verified data will enter data marketplace to be traded.
-Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform.
+Later, the verified data will enter the data marketplace to be traded.
+Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
 
@@
 
-The utility structure of IoT econimic system and game theory models are evaluated by Dusit Niyato et al.\cite{UtilityStruct}.
-Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy.
-The authors ensures the sustainability of IoT economy by game theory.
-Data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.
+The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
+They evaluated the utility structure of data trading and presented game theory model with the utility structure which provides a way to find out the Nash Equilibrium.
+The existence of Nash Equilibrium can help us to determine if the policy of the decentralized data marketplace can ensure a sustainable system.
 However, few things didn't be mentioned in their work including refund and subscription economy.
@@
 The previous work proposed different solution to specific issues of data marketplace.
-In this paper, we proposed an  overall design of decentralized data markeplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.
+In this paper, we proposed an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.
 
@@
 \subsubsection{Registrar}
-Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.
+The registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.
 
@@
 Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers.
-They decide the subscription period, subscription price, data type, sampling frequency.
-Afterward, they can launch the product on the decentralized data marketplace.
-Next, they collect raw data and send to the broker who assists in uploading data to the network.
-An MAM channel\cite{MAM} is used to store encrypted data stream.
-They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
+They can launch the product on the decentralized data marketplace and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
 
@@
 So they look forward to purchasing the streaming data from data providers.
-They search products on the marketplace and pay for subscription fee.
-While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically.
-The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains streaming data.
 
@@
 Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power.
-Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}.
-Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption.
-Then the broker provides the matching service for data provider’s products and consumer’s queries.
-After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+Once a data provider wants to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
 For each products, brokerage fees will be charged by the broker.
@@
 
-However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
-It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel.
-Furthermore, a session key can be provided to control the visibility and access to a MAM channel.
+However, MAM resolves this problem, it publishes messages to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one.
+One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, the more messages one wants to send in a channel, the more computation power is needed during creation.
+Thus data providers should decide how to distribute product into MAM channel by evaluating the cost.
+Furthermore, a session key can be provided to control the visibility and access to the data on MAM channel.
 
@@
 
-Data provider would receive subscription fee for buying data each time the data is transmitted to consumer; unpaid subscription fee would be stored in smart contract.
-The consumer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, which we called these data as decent data.
-Once the accuracy is lower than a certain accuracy, which we called it as unacceptable data, the consumers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
+The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
+Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.
+
+Refund is a major issue in our research.
+However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
+The subscription fee will be paid as new data is transmitted to consumers.
+In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
+For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
 
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
 Only one Registration Contract is needed, and everyone can query the participants' public keys.
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{registration_contract}
-    \caption{Registration Contract.}
-    \label{fig:registration_contract}
-\end{figure}
+\subsection{Launching and Searching Products}
 
-\subsection{Launching and Searching Products}
+To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
+Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
 
@@
 	\centering
-    \includegraphics[width=0.5\textwidth]{launching_product}
+	\includegraphics[width=0.4\textwidth]{launching_product}
 	\caption{The process of launching a product.}
@@
 \end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{product_contract}
-    \caption{Product Contract.}
-    \label{fig:product_contract}
-\end{figure}
-
-To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).
-Each product has a Product Contract to record the trading process.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{trading_product}
+    \includegraphics[width=0.4\textwidth]{trading_product}
     \caption{The process of the product trading.}
@@
 The whole trading process is shown in Figure \ref{fig:trading_product}.
-Once a consumer who want to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
-To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+Once a consumer who wants to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
+Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
 
-The data provider requests the consumers list maintained by the Product Contract and obtains accounts of each consumer.
-After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts.
+The data provider can obtain public keys of each consumer from the Registration Contract.
 For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
@@
 
+On the other hand, we would consider the situation that one of the consumers requests a refund in our future work.
+When the consumer is disappointed with the data quality, it may request a refund.
+Its permit should be cancelled while other consumers are unaffected.
+
 \subsection{Game Theory Evaluation}
-\subsubsection{Repeated Game}
-Repeated game consists of serveral repetitions of some stage games.
-In each stage game, the action player takes will effect the actions that players are going to take in the future stages.
-Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff.
-Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.
+Game Theory is a methodology to discuss strategic interaciton among game players.
+If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace.
+Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing.
+To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.
 
-\subsubsection{Model Description}
-We use a repeated game to express the scenario of our Data Marketplace.
 Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
@@
 The sum of all the subscription fee pays to data provider is denoted as $P_s$.
-
-Refund is a major issue in our research.
-However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
-The subscription fee will be paid as data provider provides new data.
-In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to consumers' account.
-For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
 
@@
 If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
+    \item  We assume the number of dishonest consumers is really small, so it can be negleted.
 \end{itemize}
@@
 \begin{equation} \label{payoff}
-    \sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
+    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
 \end{equation}
 
-\begin{itemize}
-    \item $P_s$ is the sum of subscription price (fee) for all subscriber.
-    \item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
-    \item $\beta$ is discounted factor.
-    \item $n$ is how many round for one maintenance period.
-    \item $m$ is how many maintenance periods have been experienced in this repeated game.
-\end{itemize}
+Al-Fagih et al.
+presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
+We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.
+We will discuss more in the next section.
 
-Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
-We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
-(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.
+\subsubsection{Numerical Example}
+To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as function of $P_r$ respectively.
+Therefore, the sum of subscription fee of all subscriber can be expressed as
+
+\begin{equation} \label{sub_fee}
+P_s = R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}
+\end{equation}
+
+where $a$ and $b$ are tuning factors, and $R$ is the maximun data value.
+And we would express the cost of maintenance as
+
+\begin{equation} \label{C_mtn}
+C_{maintain} = ce^{P_r - d}
+\end{equation}
+Where $c$ and $d$ is tuning factor.
+
+Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
+\begin{equation} \label{payoff_Pr}
+\sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
+\end{equation}
+
+Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and there is only one maintenance period has happened and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
+Based on these parameters, we can plot the payoff function as function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
+The maximun point occurs at $accuracy \approx 92\%$ which we point it out with red dot.
+\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
+    \label{fig:payoff_pic} \end{figure}
+
+Figure.\ref{fig:payoff_pic} illustratres the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is mush less than moderate quality data.
+Second the great deficit at high accuracy is mostly drived by the rapid increasing of maintenance cost.
+Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
 

### 2019-09-08 paper.tex
Add todo in Refunding
Reduce the content of Participants

@@
 
+On the other hand, we would consider the situation that one of the consumers requests a refund in our future work.
+When the consumer is disappointed with the data quality, it may request a refund.
+Its permit should be cancelled while other consumers are unaffected.
+
 \subsection{Game Theory Evaluation}

### 2019-09-08 paper.tex

--- 2019-09-08 paper.tex
@@
 \begin{equation} \label{payoff}
-    \sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
+    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
 \end{equation}
@@
 Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
+presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
 We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
-(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.
+(\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.
+We will discuss more in the next section.
+
+\subsubsection{Numerical Example}
+To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as function of $P_r$ respectively.
+Therefore, the sum of subscription fee of all subscriber can be expressed as
+
+\begin{equation} \label{sub_fee}
+P_s = R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}
+\end{equation}
+
+where $a$ and $b$ are tuning factors, and $R$ is the maximun data value.
+And we would express the cost of maintenance as
+
+\begin{equation} \label{C_mtn}
+C_{maintain} = ce^{P_r - d}
+\end{equation}
+Where $c$ and $d$ is tuning factor.
+
+Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
+\begin{equation} \label{payoff_Pr}
+\sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
+\end{equation}
+
+Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and there is only one maintenance period has happened and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
+Based on these parameters, we can plot the payoff function as function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
+The maximun point occurs at $accuracy \approx 92\%$ which we point it out with red dot.
+\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
+    \label{fig:payoff_pic} \end{figure}
+
+Figure.\ref{fig:payoff_pic} illustratres the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is mush less than moderate quality data.
+Second the great deficit at high accuracy is mostly drived by the rapid increasing of maintenance cost.
+Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
 

### 2019-09-09 paper.tex

@@
 
-Data provider would receive subscription fee for buying data each time the data is transmitted to consumer; unpaid subscription fee would be stored in smart contract.
-The consumer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, which we called these data as decent data.
-Once the accuracy is lower than a certain accuracy, which we called it as unacceptable data, the consumers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.
+The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
+Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.
+
+Refund is a major issue in our research.
+However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
+The subscription fee will be paid as new data is transmitted to consumers.
+In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
+For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
 
@@
 \subsection{Game Theory Evaluation}
-\subsubsection{Repeated Game}
-Repeated game consists of serveral repetitions of some stage games.
-In each stage game, the action player takes will effect the actions that players are going to take in the future stages.
-Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff.
-Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.
+Game Theory is a methodology to discuss strategic interaciton among game players.
+If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace.
+Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing.
+To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.
 
-\subsubsection{Model Description}
-We use a repeated game to express the scenario of our Data Marketplace.
 Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
@@
 \end{equation}
-
-\begin{itemize}
-    \item $P_s$ is the sum of subscription price (fee) for all subscriber.
-    \item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
-    \item $\beta$ is discounted factor.
-    \item $n$ is how many round for one maintenance period.
-    \item $m$ is how many maintenance periods have been experienced in this repeated game.
-\end{itemize}
 

### 2019-09-09 paper.tex
Remove redundant words

@@
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
 Only one Registration Contract is needed, and everyone can query the participants' public keys.

### 2019-09-09 paper.tex
Edit Participants and Trading Model

@@
 \subsubsection{Data Provider}
-Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers.
-They can launch the product on the decentralized data marketplace and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
+Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
 
@@
 \subsubsection{Broker}
-Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power.
-Once a data provider wants to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
-For each products, brokerage fees will be charged by the broker.
+Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource.
+Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
+Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+For each product, brokerage fees will be charged by the broker.
 
@@
 \subsubsection{Blind Signature}
+ It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
+Therefore, Blind signature is used to prevent the situation.
 Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
@@
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
-Only one Registration Contract is needed, and everyone can query the participants' public keys.
-Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
-Anyone who would like to sell or purchase data may register to become the data providers or consumers.
+At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
+Everyone can query participants' public keys.
+Those who would like to sell or purchase data may register to become the data providers or consumers.
 The registrar has the authority to agree with applications.
@@
 \subsection{Launching and Searching Products}
-
 To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
@@
 Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
-However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
-Therefore, Blind signature is used to prevent the situation.
 Figure \ref{fig:key_certification} shows the certification process.
@@
 \subsection{Trading}
+The whole trading process is shown in Figure \ref{fig:trading_product}.
+Once a consumer who wants to subscribe the streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
 
@@
 
+Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+The data provider can obtain public keys of each consumer from the Registration Contract.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
+Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
+
 \begin{figure}[h]
@@
 
-The whole trading process is shown in Figure \ref{fig:trading_product}.
-Once a consumer who wants to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
-Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
-
-The data provider can obtain public keys of each consumer from the Registration Contract.
-For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
-
 Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted data is uploaded to the MAM channel, and consumers can download and decrypt it with the session key.
+Afterward, encrypted data is published to the MAM channel, and consumers can obtain and decrypt it with the session key.
 
@@
 It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee.
-To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel.
+To protect consumer rights, the subscription fee are not transfered to the data provider until data is generated and uploaded to the MAM channel.
 If the expected data is not available, consumers can ask for refunds.

### 2019-09-10 paper.tex
Update diagrams
Edit System Architecture

--- 2019-09-09 paper.tex
@@
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who upload data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process.
 
@@
     \includegraphics[width=0.4\textwidth]{system_design}
-    \caption{System Design.}
+    \caption{The system design of a decentralized architecture which consist of a registrar, data providers, consumers and brokers.}
     \label{fig:system_design}

### 2019-09-11 paper.tex
Modify descryption

--- 2019-09-09 paper.tex
@@
 \section*{\normalsize\textbf{Abstract}}
-Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry.
+Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry.
 But IoT cannot be considered a mere extension of DaaS.
-Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability.
+Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability.
 Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
 
-In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers.
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers.
 This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
-In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform.
-Later, the verified data will enter the data marketplace to be traded.
-Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
+In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform.
+Later, the verified data will enter data marketplace to be traded.
+Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
 
@@
 The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
-They evaluated the utility structure of data trading and presented game theory model with the utility structure which provides a way to find out the Nash Equilibrium.
-The existence of Nash Equilibrium can help us to determine if the policy of the decentralized data marketplace can ensure a sustainable system.
-However, few things didn't be mentioned in their work including refund and subscription economy.
+They evaluated the utility structure of data trading and presented game theory model.
+Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure.
+However, refund and subscription economy were not mentioned in their work.
 
@@
 \section{\normalsize\textbf{Trading Model}}
-In the following, we describe the data trading process in detail.
+In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model.
 To participate a data marketplace, data providers and consumers have to register first.
@@
 \subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
+At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys.
 Only one Registration Contract is needed, and everyone can query the participants' public keys.
@@
 Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing.
-To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.
+We choose repeated game to build our game theory model.
+Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.
 
@@
     \label{fig:decision_tree} \end{figure}
-For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns.
+For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that data provider owns.
 We call this as a maintain period.
@@
 We have these following assumptions:
-\begin{itemize}
-    \item  There is no any other data providers provide the same product in Data Marketplace.
-Therefore, we can consider each provider's behavior independently.
+\begin{enumerate}
+    \item  We assume consumers are rational. \label{rational_man}
+    \item  Each data provider monopoly of the product they produced. \label{monopoly}
+    \item  Subscription fee only depends on data quality. \label{fee_vs_quality}
+    \item  At least 51\% of consumers are in the same group which has complete information exchange.\label{51_in_group} 
+    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. \label{1_in_51}
+\end{enumerate}
+
+According to \textbf{assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational.
+
+\textbf{Assumption(\ref{monopoly})} implies there is no other data providers provide the same product in Data Marketplace.
+In this way, we can consider each provider's behavior independently.
 That means this decision tree represent the behavior of only one data provider.
-    \item  More than 51\% of consumers are among complete information exchange state.
-In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
-    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality.
-If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
-    \item  We assume the number of dishonest consumers is really small, so it can be negleted.
-\end{itemize}
+
+From \textbf{assumption(\ref{51_in_group})}, we derive one thing that once one of any consumer in that group launches voting for stopping buying data (in other words, the comsumer annonces the data quality is not acceptable), they would succeed in rejecting the processing subscription.
+
+\textbf{Assumption(\ref{1_in_51})}  implies if unacceptably low accuracy data are delivered to consumers, the examiner will spread this information out.
 
@@
 (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.
-We will discuss more in the next section.
 
@@
 Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers.
-However, the auction process between multiple participants and analyzing potential threats are still critical issues that need to be resolved.
+However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved.
+The game theory model presented in this work, we assume each data provider's behavior is independent.
+However, normally there would be multiple data providers provide similar product (substitution).
+Only one provider is taken into considerations at present.
 

### 2019-09-11 paper.tex
Add detailed despcription and figure in Component - MAM

--- 2019-09-09 paper.tex
@@
 
-\subsection{Component}
+\subsection{Components}
 \subsubsection{Masked Authenticated Messaging}
-IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
-The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions.
-Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.
+IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.
 
-However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
-It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel.
-Furthermore, a session key can be provided to control the visibility and access to a MAM channel.
+MAM resolves the challenge to publish encrypted streaming data to distributed ledgers.
+It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one.
+Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.
+
+One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels.
+While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
+See Figure \ref{fig:launching_product}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{launching_product}
+	\caption{The process of launching a product.}
+	\label{fig:launching_product}
+\end{figure}
 
@@
 Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{launching_product}
-	\caption{The process of launching a product.}
-	\label{fig:launching_product}
-\end{figure}
 

### 2019-09-11 paper.tex
Add citation and rewording

@@
 The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
-The Third Party Auditors (TPAs)-based frameworks is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data.
+The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data.
 Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract and Cloud Server.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server.
 Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization.
 However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers.
-Also, the performance analysis shows that IoT devices have low efficiency interacting with Etheruem due to the time-consuming Proof-of-Work(PoW) process.
+Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
 
@@
 
-On the basis of the Tangle and MAM, IOTA foundation proposed a decentralized Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM.
-Nevertheless, the platform design is centralized, new devices require manual approval from IOTA team to be visible in the marketplace.
+On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM.
+Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace.
 Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.
@@
 The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker.
-Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers.
+Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
 However, the data integrity and authentication of each participant are still future work.
@@
 The previous work proposed different solution to specific issues of data marketplace.
-In this paper, we proposed an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.
+In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.
 
@@
 
-\subsection{Components}
+\subsection{Component}
 \subsubsection{Masked Authenticated Messaging}
-IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.
+IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}.
+The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions.
+Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.
 
-MAM resolves the challenge to publish encrypted streaming data to distributed ledgers.
-It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one.
-Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.
-
-One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels.
-While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
-See Figure \ref{fig:launching_product}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{launching_product}
-	\caption{The process of launching a product.}
-	\label{fig:launching_product}
-\end{figure}
+However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
+It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel.
+Furthermore, a session key can be provided to control the visibility and access to a MAM channel.
 
@@
 \subsubsection{Ethereum Smart Contract}
-Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
+Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
 The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency.
@@
 Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{launching_product}
+	\caption{The process of launching a product.}
+	\label{fig:launching_product}
+\end{figure}
 

### 2019-09-11 paper.tex
Revise formulas and change the words "upload"

@@
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who upload data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
 
@@
 Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
-Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.
+Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel.
 For each product, brokerage fees will be charged by the broker.
@@
 The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it.
+In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of MAM channel to smart contract without knowing it.
 
@@
 Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
-In our proposed architecture, brokers are responsible to upload the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
+In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
 
@@
 It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee.
-To protect consumer rights, the subscription fee are not transfered to the data provider until data is generated and uploaded to the MAM channel.
+To protect consumer rights, the subscription fee are not transfered to the data provider until data is generated and published to the MAM channel.
 If the expected data is not available, consumers can ask for refunds.
@@
 \begin{equation}
-    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) (1-F_{t})
+    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) -F_{t}
 \end{equation}
@@
 \begin{equation}
-    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} (1-F_{t})
+    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} -F_{t}
 \end{equation}
@@
 \begin{equation}
-    F_{Consumer}(i) = price \frac{M-i+1}{M} (1-F_{t})
+    F_{Consumer}(i) = price \frac{M-i+1}{M} -F_{t}
 \end{equation}
 
-where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of consumers in this contract.
+where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract.
 
 To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee.
-We assume that only a half of the expected records are uploaded to the MAM channel.
-For the data provider and broker, they can withdraw a half of total subscription fee from the smart contract and $F_{b}$ \% belongs to the broker while the remaining belongs to the data provider.
+We assume that only a half of the expected records are published to the MAM channel.
+When $F_{b}$ is 5\%, the data provider and broker can withdraw a half of total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
 For consumers, they can get a half refund which should be deducted the transaction fee.

### 2019-09-12 paper.tex
Modify related work
* Replace blockchain with DLT
* Mention why DLT is a solution
* Add MAM feature

@@
 The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
-The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data.
-Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.
+The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data.
+Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
 
@@
 By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit and access an encrypted data stream over the Tangle where privacy and integrity meet.
+On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.
 

### 2019-09-14 paper.tex
Grammar tweak and component MAM rearrangement

@@
 \section*{\normalsize\textbf{Abstract}}
-Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry.
-But IoT cannot be considered a mere extension of DaaS.
-Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability.
+Transacting IoT data must be different in many respects to build much-needed trust in data marketplaces, trust that will be key to their sustainability.
 Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
-
-In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers.
-This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
-In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform.
-Later, the verified data will enter the data marketplace to be traded.
+In this paper, we propose a novel approach to construct IoT-enabled data marketplace by decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers.
+It can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
+Storage via an end-to-end encrypted message channel allows emitting and accessing trusted data stream over the distributed ledgers regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform.
 Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
-
 \begin{IEEEkeywords}
@@
 The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution.
-As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
-This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems.
+As physical assets such as ships, factories, vehicles, farms and buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
+This paradigm shift will be more complex to administer, forcing businesses to rethink their competitive play as part of these ecosystems.
 Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
@@
 \begin{enumerate}
-    \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
+    \item Data owners do not have much control over their data and their data is locked in silos managed by products and services companies.
     \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
@@
 
-To overcome these barriers, we implement IoT-enabled Data Marketplace and sensor data submission functionalities are intended to be very lightweight, capable of running on embedded devices.
+To overcome these barriers, we implemented IoT-enabled data marketplace and sensor data submission functionalities which are intended to be very lightweight and capable of running on embedded devices.
 They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
@@
 
-Take the use case of Airbox\cite{LASS} for instance.
-Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
+Take the use case of the Airbox\cite{LASS} for instance.
+Every household with an Airbox device can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
 To protect privacy, data should be encrypted before on-chain.
-As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction.
+As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to write down every transaction.
 At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
 Last but not least, payments will be stored on the smart contracts until the transactions are confirmed.
-The whole sequence is illustrated in Figure \ref{fig:airbox}.
+The entire sequence is illustrated in Figure \ref{fig:airbox}.
 
@@
 \section{\normalsize\textbf{Related Work}}
-The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
+As the economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
 The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data.
-Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
+Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technologies (DLTs) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server.
-Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization.
-However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers.
-Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
+Data Integrity as a Service (DIaaS) is a blockchain-based framework for data integrity proposed by Liu et al.,\cite{DIaas} which is a Cloud Server Service (CSS) and allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and penalization.
+However, the architecture of DIaaS needs high trust on the CSS.
+If CSS is malicious or has crashed, losses to both providers and consumers will result.
+Also, performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
 
-By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.
+To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
+Based on Tangle, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.
 
-On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM.
-Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace.
-Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.
+Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protected and assurance of data integrity from source with MAM.
+Nevertheless, the platform design is centralized, new devices require manual approval from the IOTA foundation to be visible in the marketplace.
+Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.
 
 A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned.
-The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker.
-Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
-However, the data integrity and authentication of each participant are still future work.
+The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers.
+The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
+However, the data integrity and authentication of each participant is still forthcoming.
 
-The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
+The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
 They evaluated the utility structure of data trading and presented game theory model.
 Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure.
-However, refund and subscription economy were not mentioned in their work.
+However, refund and subscription mechanism were not mentioned in their work.
 
-The previous work proposed different solution to specific issues of data marketplace.
-In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.
+Such work proposed different solutions to specific issues of data marketplaces.
+In this paper, we have an overall design of decentralized data marketplace that handles data integrity and trading procedures, such as buyout and subscibing to future data on distributed ledgers.
 
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
+Our proposed data marketplace framework is a 3-tier de-centralized architecture with registrars, data providers, data consumers and brokers.
 
@@
 \subsubsection{Registrar}
-The registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.
+The registrars are responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.
 
@@
 \subsubsection{Consumer}
-Consumers aspire to obtain streaming data to promote the value of their service.
-However, it is a big challenge for most consumers to collect the desired data by themselves.
-So they look forward to purchasing the streaming data from data providers.
+Consumers aspire to obtain streaming data to improve the value of their service.
+However, it is a significant challenge for most consumers to collect the desired data by themselves.
+So they look to purchasing the streaming data from data providers.
 
 \subsubsection{Broker}
-Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource.
-Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
-Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel.
+Brokers delegate data providers and consumers to perform computing tasks as brokers are expected to have ample resources.
+Trustworthy brokers that meet the requirement of the  conformity assessment are added to the decentralized data marketplace.
+Once a qualified data provider requests to launch a new product, the broker would deal the trading process and publish the their data streams to the MAM channel.
 For each product, brokerage fees will be charged by the broker.
@@
 \subsubsection{Masked Authenticated Messaging}
-IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.
+MAM is a second layer data communication protocol built on the feeless and scalable IOTA network.
+It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one.
+In other words, with channel root (aka the first message of a channel) and its session key, all data becomes accessible and validatable.
+Furthermore, each user can create multiple channels as possible.
+See Figure \ref{fig:mam_channel}
 
-MAM resolves the challenge to publish encrypted streaming data to distributed ledgers.
-It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one.
-Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.4\textwidth]{mam_channel}
+    \caption{A user could create multiple MAM channels}
+    \label{fig:mam_channel}
+\end{figure}
 
-One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels.
-While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
-See Figure \ref{fig:launching_product}
+\subsubsection{TangleID}
+The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
+With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
+Posting DID documents on MAM makes TangleID a GDPR-Complianced system.
+Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
+
+\subsubsection{Ethereum Smart Contract}
+Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
+The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+All conditions and states established in the contract are enforeced with transparency.
+The appearance of smart contracts meet different requirements of trading pattern.
+
+\subsubsection{Blind Signature}
+Blind signature\cite{blindSig} is used to prevent the situation that the a broker would stole data if a session key is not encryted.
+In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm.
+The encrypted message, along with the blinding factor, can be later verified with the signer’s public key.
+In our design, brokers would perform blind signature during the process of adding new products for data providers, in order to send session keys of MAM channel to smart contract without knowing it.
+
+\subsubsection{IPFS}
+Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
+In our proposed architecture, brokers are responsible for publishing metadata to IPFS, including titles, data provider information and data preview, in order to provide users with searching capabilities.
+
+\section{\normalsize\textbf{Trading Model}}
+In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model.
+To participate a data marketplace, data providers and consumers have to register first.
+Then data provider can launch its product on the marketplace.
+Once a product is launched, it is searchable and can be subsequently traded.
+The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
+
+The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
+Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.
+
+Refunds are a major issue in our research.
+However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
+The subscription fee will be paid as new data is transmitted to consumers.
+In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
+For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
+
+\subsection{Participants Registration}
+At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
+Everyone can query participants' public keys.
+Those who would like to sell or purchase data may register to become a data provider or consumer.
+The registrar has the authority to agree with applications.
+After that, their identities are available in the Registration Contract and the launching and trading processes can begin.
+
+\subsection{Launching and Searching Products}
+To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. 
+MAM allows users to create multiple channels as possible, however, the size of a channel is fixed which is decided before creation.
+Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new MAM channel and Product Contract for recording the participants, subscription price brokerage fee, quantity of data and trading process.
 
@@
 
-\subsubsection{TangleID}
-TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
-With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.
-
-\subsubsection{Ethereum Smart Contract}
-Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
-The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and with enforcement.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
-
-\subsubsection{Blind Signature}
- It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
-Therefore, Blind signature is used to prevent the situation.
-Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of MAM channel to smart contract without knowing it.
-
-\subsubsection{IPFS}
-Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
-In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
-
-\section{\normalsize\textbf{Trading Model}}
-In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model.
-To participate a data marketplace, data providers and consumers have to register first.
-Then data provider can launch its product on the marketplace.
-Once a product is launched, it is searchable and could be traded afterward.
-The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
-
-The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
-Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.
-
-Refund is a major issue in our research.
-However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
-The subscription fee will be paid as new data is transmitted to consumers.
-In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
-For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
-
-\subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
-Everyone can query participants' public keys.
-Those who would like to sell or purchase data may register to become the data providers or consumers.
-The registrar has the authority to agree with applications.
-After that, their identities are available in the Registration Contract and launching and trading processes can be started.
-
-\subsection{Launching and Searching Products}
-To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
-Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
-
 Brokers certify session keys as well.
-Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
+Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers.
 Figure \ref{fig:key_certification} shows the certification process.
-When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
+When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
 Then the data provider sends the blinded session key $Blind(k)$ to the broker.
@@
 Consumers can search the desired product by keywords or tags.
-The consumer then evaluates the product and start trading with the data provider if the consumer is interested in subscribing the data.
+The consumer then evaluates the product and initiates the trading with the data provider if the consumer is interested in subscribing to the data.
 
 \subsection{Trading}
-The whole trading process is shown in Figure \ref{fig:trading_product}.
-Once a consumer who wants to subscribe the streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
+The entire trading process is as shown in Figure \ref{fig:trading_product}.
+Once a consumer who wants to subscribe certain streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
 
@@
 	\includegraphics[width=0.4\textwidth]{trading_product}
-	\caption{The process of the product trading.}
+	\caption{The process for the product trading.}
 	\label{fig:trading_product}
@@
 
-Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}.
 The data provider can obtain public keys of each consumer from the Registration Contract.
 For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.
+Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
 
@@
 It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee.
-To protect consumer rights, the subscription fee are not transfered to the data provider until data is generated and published to the MAM channel.
-If the expected data is not available, consumers can ask for refunds.
-We assume that less than half of consumers in the Product Contract are irrational and malicious.
-Each consumer can vote for refunding at any time.
-If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer.
+To protect consumer rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel.
+If the expected data is not available, consumers can request refunds.
+We assume that a very small percentage of consumers in the Product Contract are irrational and/or malicious.
+Each consumer can vote for a refund at any time.
+If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
 The subscription fee can be prorated as below:
@@
 When $F_{b}$ is 5\%, the data provider and broker can withdraw a half of total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
-For consumers, they can get a half refund which should be deducted the transaction fee.
+For consumers, they can get half of the subscription fee refunded which should be deducted the transaction fee.
 
@@
 Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing.
-We choose repeated game to build our game theory model.
+We employed repeated game to build our game theory model.
 Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.

### 2019-09-14 paper.tex
Refactor Component

@@
 \subsubsection{Registrar}
-The registrars are responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.
+Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.
 
 \subsubsection{Data Provider}
-Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
+Data providers generate and preserve streaming data. With the profit through trading process, they can improve the quality and quantity of data.
 
@@
 Consumers aspire to obtain streaming data to improve the value of their service.
-However, it is a significant challenge for most consumers to collect the desired data by themselves.
+However, it is a significant challenge and cost to collect the desired data by themselves.
 So they look to purchasing the streaming data from data providers.
@@
 Trustworthy brokers that meet the requirement of the conformity assessment are added to the decentralized data marketplace.
-Once a qualified data provider requests to launch a new product, the broker would deal the trading process and publish the their data streams to the MAM channel.
-For each product, brokerage fees will be charged by the broker.
+Once a qualified data provider requests to launch a new product, the broker would charge brokerage fees to deal the trading process and publish their data streams to the MAM channel.
 
@@
 \subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
-With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
-Posting DID documents on MAM makes TangleID a GDPR-Complianced system.
-Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
+The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprints.
+TangleID converts digital footprints into Decentralized Identifiers (DIDs)\cite{DID}Documents defined by W3C and publishes to MAM channels.
+Each participant is required to register on TangleID and performs digital signature with key pairs recorded on DID Documents, thus participants' identity could be easily verified and data persistency of a product could be ensured.
 
@@
 The encrypted message, along with the blinding factor, can be later verified with the signer’s public key.
-In our design, brokers would perform blind signature during the process of adding new products for data providers, in order to send session keys of MAM channel to smart contract without knowing it.
 

### 2019-09-14 paper.tex
Refactor Trading Model introduction section

--- 2019-09-14 paper.tex
@@
 \section{\normalsize\textbf{Trading Model}}
-In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model.
+In the following, we describe the data trading process in detail and adapt game theory to ensure the sustainability of our tading model.
 To participate a data marketplace, data providers and consumers have to register first.
@@
 
-The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
-Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.
-
-Refunds are a major issue in our research.
-However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
-The subscription fee will be paid as new data is transmitted to consumers.
-In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
-For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
+To evaluate trading model with game theory, we divide every piece of data products into two categories by the quality and accuracy, the \textbf{decent data} that consumers are willing to buy and \textbf{unacceptable data} that consumers would stop buying.
+Though refund is a major topic in our research, it is not discussed in game theory evaluation section.
+Since consumers pay off once to Purchase Contract for each merchandise, the subscription fee is either paid to providers or returned automatically.
+That is, both providers and consumers do not charge for extra fees during refund process.
 
@@
 At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
-Everyone can query participants' public keys.
-Those who would like to sell or purchase data may register to become a data provider or consumer.
-The registrar has the authority to agree with applications.
-After that, their identities are available in the Registration Contract and the launching and trading processes can begin.
+Everyone can query others' public keys for validation but only registrars have permission to add new members.
+After registration, the launching and trading processes can begin.
 
@@
 MAM allows users to create multiple channels as possible, however, the size of a channel is fixed which is decided before creation.
-Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new MAM channel and Product Contract for recording the participants, subscription price brokerage fee, quantity of data and trading process.
+Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new one and a  Product Contract that records the participants, subscription price, brokerage fee, MAM channel session key, quantity of data and trading process.
 

### 2019-09-14 paper.tex
Revise wording

--- 2019-09-14 paper.tex
@@
 \section{\normalsize\textbf{Related Work}}
-The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
-The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data.
+As the economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
+The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format dynamic nature of IoT data.
 Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server.
-Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization.
-However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers.
-Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) which allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
+However, the architecture of DIaaS needs high trust on the CSS.
+If the CSS is malicious or has crashed, losses to both providers and consumers will result.
+Also, performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
 
-By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.
+To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
+On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.
 
-On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM.
-Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace.
-Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.
+Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protected and assurance of data integrity from source with MAM.
+Nevertheless, the platform design is centralized, new devices require manual approval from the IOTA foundation to be visible in the marketplace.
+Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.
 
 A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned.
-The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker.
-Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
-However, the data integrity and authentication of each participant are still future work.
+The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers.
+The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
+However, the data integrity and authentication of each participant is still forthcoming.
 
-The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
+The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
 They evaluated the utility structure of data trading and presented game theory model.
@@
 
-The previous work proposed different solution to specific issues of data marketplace.
-In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.
+Such work proposed different solutions to specific issues of data marketplaces.
+In this paper, we had an overall design of decentralized data marketplace that handles data integrity and trading procedures such as buyout and subscriptions to future data on a distributed ledger.
 

### 2019-09-14 paper.tex
Revise wording

@@
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to post participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
 
@@
 Consumers aspire to obtain streaming data to promote the value of their service.
-However, it is a big challenge for most consumers to collect the desired data by themselves.
-So they look forward to purchasing the streaming data from data providers.
+However, it is a significant challenge for most consumers to collect the desired data by themselves.
+So they look to purchasing the streaming data from data providers.
 
 \subsubsection{Broker}
-Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource.
+Brokers represent data providers and consumers to perform computing tasks as brokers are expected to have higher resource.
 Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
 Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel.
-For each product, brokerage fees will be charged by the broker.
+Brokerage fees for each product will be charged by the broker.
 
@@
 \subsubsection{TangleID}
-TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
-In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system.
-With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.
+The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
+With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
+Posting DID documents on MAM makes TangleID a GDPR-Complianced system.
+Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
 
 \subsubsection{Ethereum Smart Contract}
-Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract.
-The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency.
+Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
+The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
 All conditions and states established in the contract are transparent and with enforcement.
@@
 The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of MAM channel to smart contract without knowing it.
+In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of the MAM channel to smart contract without knowing it.
 
@@
 Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
-In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
+In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to the IPFS in order to provide users with search capabilities to meet the consumers' need.
 

### 2019-09-14 paper.tex
Revise wording

@@
 \subsubsection{Blind Signature}
- It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss.
-Therefore, Blind signature is used to prevent the situation.
+ It is a risk revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
+Therefore, a blind signature is used to prevent session key copying for such circumstances.
 Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
@@
 Then data provider can launch its product on the marketplace.
-Once a product is launched, it is searchable and could be traded afterward.
+Once a product is launched, it is searchable and can be subsequently traded.
 The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
 
-The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
-Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.
+The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
+Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.
 
-Refund is a major issue in our research.
+Refunds are a major issue in our research.
 However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
@@
 Everyone can query participants' public keys.
-Those who would like to sell or purchase data may register to become the data providers or consumers.
+Those who would like to sell or purchase data may register to become a data provider or consumer.
 The registrar has the authority to agree with applications.
-After that, their identities are available in the Registration Contract and launching and trading processes can be started.
+After that, their identities are available in the Registration Contract and the launching and trading processes can begin.
 
 \subsection{Launching and Searching Products}
-To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
 The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
@@
 Brokers certify session keys as well.
-Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.
+Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers.
 Figure \ref{fig:key_certification} shows the certification process.
-When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
+When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
 Then the data provider sends the blinded session key $Blind(k)$ to the broker.

### 2019-10-17 paper.tex
Indent
Statement and grammar tweak

@@
 \section*{\normalsize\textbf{Abstract}}
-Transacting IoT data must be different in many respects to build much-needed trust in data marketplaces, trust that will be key to their sustainability.
-Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.
-In this paper, we propose a novel approach to construct IoT-enabled data marketplace by decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers.
-It can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain.
-Storage via an end-to-end encrypted message channel allows emitting and accessing trusted data stream over the distributed ledgers regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform.
-Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
+Transacting IoT data must be different in many from traditional approaches in order to build much-needed trust in data marketplaces—trust that will be key to their sustainability.
+Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making.
+In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
+This approach can efficiently enhance the degree of transparency, as all interactions with smart contracts will be written on-chain.
+Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform.
+Furthermore, the platform will complete matching, trading and refunding processes without human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
 \begin{IEEEkeywords}
@@
 As physical assets such as ships, factories, vehicles, farms and buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
-This paradigm shift will be more complex to administer, forcing businesses to rethink their competitive play as part of these ecosystems.
+This paradigm shift will be more complex to administers, forcing businesses to rethink their competitive play as part of these ecosystems.
 Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
@@
 
-Take the use case of the Airbox\cite{LASS} for instance.
-Every household with an Airbox device can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities.
-To protect privacy, data should be encrypted before on-chain.
-As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to write down every transaction.
+Looking at Airbox\cite{LASS} as an example, every household with an Airbox device can collect air quality records automatically and autonomically—rather than passively receive the outcomes from the centralized authorities.
+To protect privacy, data should be encrypted before going on-chain.
+As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to record every transaction.
 At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
@@
 \section{\normalsize\textbf{Related Work}}
-As the economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace.
-The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format dynamic nature of IoT data.
-Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
+As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace.
+The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
+Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) which allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
 Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
@@
 If the CSS is malicious or has crashed, losses to both providers and consumers will result.
-Also, performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
+Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
 
@@
 
-Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protected and assurance of data integrity from source with MAM.
-Nevertheless, the platform design is centralized, new devices require manual approval from the IOTA foundation to be visible in the marketplace.
+Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protection and assurance of data integrity from the source with MAM.
+Nevertheless, the platform design is centralized, where new devices require manual approval from the IOTA foundation to be visible in the marketplace.
 Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.
@@
 
-The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
-They evaluated the utility structure of data trading and presented game theory model.
-Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure.
-However, refund and subscription economy were not mentioned in their work.
+The sustainability of IoT economic system was discussed by Dusit Niyato et al.\cite{UtilityStruct}.
+They evaluated the utility structure of data trading and presented a game theory model.
+Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found via game theory and its utility structure.
+However, refund and subscription economies were not mentioned in their work.
 
 Such work proposed different solutions to specific issues of data marketplaces.
-In this paper, we had an overall design of decentralized data marketplace that handles data integrity and trading procedures such as buyout and subscriptions to future data on a distributed ledger.
+In this paper, we propose an overall design of decentralized data marketplace that handles data integrity and trading procedures such as buyout and subscriptions to future data on a distributed ledger.
 
@@
 Consumers aspire to obtain streaming data to promote the value of their service.
-However, it is a significant challenge for most consumers to collect the desired data by themselves.
-So they look to purchasing the streaming data from data providers.
+However, it is a significant challenge for most consumers to collect the desired data by themselves, so they look to purchasing the streaming data from data providers.
 
@@
 MAM resolves the challenge to publish encrypted streaming data to distributed ledgers.
-It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one.
-Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.
+It publishes messages encrypted with a \textbf{session key} to the \textbf{channel}, which is a form of transaction where each address can be derived from the previous one.
+Therefore, with each \textbf{channel root}—the first message of a channel and the session key—all data on the channel is accessible.
 
-One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels.
+One can create multiple channels, however, the size of a channel is fixed which is decided before creation.
+Thus data providers need to firstly decide how to distribute data product into MAM channels.
 While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
@@
 \subsubsection{Blind Signature}
- It is a risk revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
+There is inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
 Therefore, a blind signature is used to prevent session key copying for such circumstances.
@@
 The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of the MAM channel to smart contract without knowing it.
+In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.
 
 \subsubsection{IPFS}
-Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users.
+Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but is with all IPFS users.
 In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to the IPFS in order to provide users with search capabilities to meet the consumers' need.
@@
 \section{\normalsize\textbf{Trading Model}}
-In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model.
+In the following, we describe the data trading process in detail where we use game theory to ensure the sustainability of our trading model.
 To participate a data marketplace, data providers and consumers have to register first.
@@
 Refunds are a major issue in our research.
-However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data.
+However, we do not need to take refund as a factor in our game theory model, since in our decentralized data marketplace we use a smart contract to store the subscription fee which will be paid to buy the future data.
 The subscription fee will be paid as new data is transmitted to consumers.
-In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account.
-For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.
+In other words, the data provider does not need to perform any procedures to transfer subscription fees from his/her own account to consumers' accounts.
+For the same reason, data providers have no responsibility on refunding processing fees charged by the smart contract.
 
-\subsection{Participants Registration}
-At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
-Everyone can query participants' public keys.
+\subsection{Participant Registration}
+At the beginning, the egistrar creates a registration contract, which maintains all participants' information, including their DID documents and public keys.
+Anyone can query participants' public keys.
 Those who would like to sell or purchase data may register to become a data provider or consumer.
 The registrar has the authority to agree with applications.
-After that, their identities are available in the Registration Contract and the launching and trading processes can begin.
+After that, their identities are available in the registration contract and the launching and trading processes can begin.
 
@@
 To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
-The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.
-Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
+The data provider determines a trusted broker and asks the broker to create a new MAM channel and product contract.
+Each product has a product contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.
 
@@
 The entire trading process is as shown in Figure \ref{fig:trading_product}.
-Once a consumer who wants to subscribe certain streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.
+Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.
 
@@
 Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}.
-The data provider can obtain public keys of each consumer from the Registration Contract.
-For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract.
+The data provider can obtain public keys of each consumer from the registration contract.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract.
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
@@
 
-Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Consumers can obtain the broker's public key on the registration contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
 Afterward, encrypted data is published to the MAM channel, and consumers can obtain and decrypt it with the session key.
@@
 If the expected data is not available, consumers can request refunds.
-We assume that a very small percentage of consumers in the Product Contract are irrational and/or malicious.
+We assume that a very small percentage of consumers in the product contract are irrational and/or malicious.
 Each consumer can vote for a refund at any time.
@@
 
-To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee.
+To refund or withdraw subscription fees from the smart contract, the data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for the transaction fee.
 We assume that only a half of the expected records are published to the MAM channel.
-When $F_{b}$ is 5\%, the data provider and broker can withdraw a half of total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
-For consumers, they can get half of the subscription fee refunded which should be deducted the transaction fee.
+When $F_{b}$ is 5\%, the data provider and broker can withdraw half of the total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
+For consumers, they can receive half of the subscription fee refunded which should be deducted from the transaction fee.
 
-On the other hand, we would consider the situation that one of the consumers requests a refund in our future work.
-When the consumer is disappointed with the data quality, it may request a refund.
-Its permit should be cancelled while other consumers are unaffected.
+Considering the situation that one of the consumers requests a refund in the future, when the consumer is disappointed with the data quality, he/she may request a refund.
 
@@
 Game Theory is a methodology to discuss strategic interaciton among game players.
-If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace.
-Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing.
-We employed repeated game to build our game theory model.
-Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.
+If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace.
+Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing.
+We employed repeated games to build our game theory model.
+Repeated games consists of several repetitions of the same base game which meets the scenario of data subscription.
 
-Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used.
-Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person.
-The sum of all the subscription fee pays to data provider is denoted as $P_s$.
+Figure.\ref{fig:decision_tree} shows the decision tree to depict the repeated game we used.
+Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, for each person.
+The sum of all the subscription fee paid to the data provider is denoted as $P_s$.
 
@@
     \label{fig:decision_tree} \end{figure}
-For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that data provider owns.
-We call this as a maintain period.
-Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.
+For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that the data provider owns.
+We call this a maintenance period.
+Moreover, the value of data and the cost of maintenance will decrease as time passes, so we introduce a discounted factor $\beta$ to depict this phenomena.
 
-We have these following assumptions:
+Following assumptions are made:
 \begin{enumerate}
     \item  We assume consumers are rational. \label{rational_man}
-    \item  Each data provider monopoly of the product they produced. \label{monopoly}
-    \item  Subscription fee only depends on data quality. \label{fee_vs_quality}
+    \item  Each data provider is the sole provider of the product they produced. \label{monopoly}
+    \item  Subscription fees only depends on data quality. \label{fee_vs_quality}
     \item  At least 51\% of consumers are in the same group which has complete information exchange.\label{51_in_group}
-    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. \label{1_in_51}
+    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine  data quality. \label{1_in_51}
 \end{enumerate}
@@
 
-\textbf{Assumption(\ref{monopoly})} implies there is no other data providers provide the same product in Data Marketplace.
+\textbf{Assumption(\ref{monopoly})} implies there is no other data providers providing the same product in the data marketplace.
 In this way, we can consider each provider's behavior independently.
-That means this decision tree represent the behavior of only one data provider.
+That means this decision tree represents the behavior of only one data provider.
 
-From \textbf{assumption(\ref{51_in_group})}, we derive one thing that once one of any consumer in that group launches voting for stopping buying data (in other words, the comsumer annonces the data quality is not acceptable), they would succeed in rejecting the processing subscription.
+From \textbf{assumption(\ref{51_in_group})}, we derive that one of any consumer in that group launches voting for stopping buying data (in other words, the consumer announces the data quality is not acceptable), they would succeed in rejecting the processing subscription.
 
@@
 Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$.
+presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is approximately an exponential function of $P_r$.
 We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
@@
 \subsubsection{Numerical Example}
-To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as function of $P_r$ respectively.
+To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as functions of $P_r$ respectively.
 Therefore, the sum of subscription fee of all subscriber can be expressed as
@@
 
-where $a$ and $b$ are tuning factors, and $R$ is the maximun data value.
+where $a$ and $b$ are tuning factors, and $R$ is the maximum data value.
 And we would express the cost of maintenance as
@@
 \end{equation}
-Where $c$ and $d$ is tuning factor.
+Where $c$ and $d$ are tuning factors.
 
@@
 
-Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and there is only one maintenance period has happened and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
-Based on these parameters, we can plot the payoff function as function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
-The maximun point occurs at $accuracy \approx 92\%$ which we point it out with red dot.
+Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and only one maintenance period has occured and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
+Based on these parameters, we can plot the payoff function as a function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
+The maximum point occurs at $accuracy \approx 92\%$ which is indicated with a red dot.
 \begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
@@
 
-Figure.\ref{fig:payoff_pic} illustratres the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
-First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is mush less than moderate quality data.
-Second the great deficit at high accuracy is mostly drived by the rapid increasing of maintenance cost.
+Figure.\ref{fig:payoff_pic} illustrates the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data.
+Second the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost.
 Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
@@
 The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers.
-While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform.
+While there has been many auction models\cite{BigPicDataMarket} in several areas, there has been minimal research on third-party auction platforms.
 Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers.
 However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved.
-The game theory model presented in this work, we assume each data provider's behavior is independent.
-However, normally there would be multiple data providers provide similar product (substitution).
+For the game theory model presented in this work, we assume each data provider's behavior is independent.
+However, normally there would be multiple data providers providing similar products (substitutions).
 Only one provider is taken into considerations at present.

### 2019-10-22 paper.tex
Cite GDPR paper for TangleID

@@
 \subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
+The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint.
 With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
-Posting DID documents on MAM makes TangleID a GDPR-Complianced system.
+Posting DID documents on MAM makes TangleID a GDPR-Complianced system\cite{GDPR}.
 Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

### 2019-10-22 paper.tex
Cite GDPR paper for TangleID

@@
 \end{enumerate}
-
-Looking at Airbox\cite{LASS} as an example, every household with an Airbox device can collect air quality records automatically and autonomically—rather than passively receive the outcomes from the centralized authorities.
-To protect privacy, data should be encrypted before going on-chain.
-As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to record every transaction.
-At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will.
-Last but not least, payments will be stored on the smart contracts until the transactions are confirmed.
-The entire sequence is illustrated in Figure \ref{fig:airbox}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{airbox}
-    \caption{IoT-enabled personal air quality assistant.}
-    \label{fig:airbox}
-\end{figure}
 
@@
 
-Figure.\ref{fig:decision_tree} shows the decision tree to depict the repeated game we used.
-Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, for each person.
-The sum of all the subscription fee paid to the data provider is denoted as $P_s$.
+Each consumer would pay subscription fee, $p_s$, each time they receive data from data provider. The sum of all the subscription fee paid to the data provider is denoted as $P_s$.
 
-\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
-    \label{fig:decision_tree} \end{figure}
 For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that the data provider owns.
@@
 
-Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
-\begin{equation} \label{payoff_Pr}
-    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
-\end{equation}
-
-Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and only one maintenance period has occured and one maintenance period consists of 12 rounds which means $m = 1, n = 12$.
-Based on these parameters, we can plot the payoff function as a function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}.
-The maximum point occurs at $accuracy \approx 92\%$ which is indicated with a red dot.
-\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
-    \label{fig:payoff_pic} \end{figure}
-
-Figure.\ref{fig:payoff_pic} illustrates the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+Substitute Eq.
+(\ref{sub_fee}) and Eq.
+(\ref{C_mtn}) into Eq.
+(\ref{payoff}).
+We can derive an equation illustrating the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
 First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data.

### 2019-10-24 paper.tex
Remove pictures and equation

--- 2019-10-22 paper.tex
@@
 \subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint.
+The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint.
 With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
-Posting DID documents on MAM makes TangleID a GDPR-Complianced system\cite{GDPR}.
+Posting DID documents on MAM makes TangleID a GDPR-Complianced system.
 Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

### 2019-10-24 paper.tex
Remove useless subtopic

--- 2019-10-22 paper.tex
@@
 Al-Fagih et al.
-presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is approximately an exponential function of $P_r$.
+presented\cite{DataPrice} the quality of data $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is approximately an exponential function of $P_r$.
 We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq.
@@
 
-\subsubsection{Numerical Example}
 To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as functions of $P_r$ respectively.

### 2019-10-24 paper.tex
Fix typo

--- 2019-10-24 paper.tex
@@
 
-Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protection and assurance of data integrity from the source with MAM.
-Nevertheless, the platform design is centralized, where new devices require manual approval from the IOTA foundation to be visible in the marketplace.
+Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protection and assurance of data integrity from the source with MAM.
+Nevertheless, the platform design is centralized, where new devices require manual approval from the IOTA Foundation to be visible in the marketplace.
 Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.
@@
     \includegraphics[width=0.4\textwidth]{system_design}
-    \caption{The system design of a decentralized architecture which consist of a registrar, data providers, consumers and brokers.}
+    \caption{The system design of a decentralized architecture which consists of a registrar, data providers, consumers and brokers.}
     \label{fig:system_design}

### 2019-10-24 paper.tex
Emphasize on decentralized identifiers

@@
 
-\subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint.
-With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
+\subsubsection{Decentralized Identifiers}
+The TangleID\cite{TangleID} is a self-sovereign identity system that does not require any third-party authority to verify an identity and its digital footprint.
+With it, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
 Posting DID documents on MAM makes TangleID a GDPR-Complianced system\cite{GDPR}.

### 2019-10-24 paper.tex
Simplify mission statement

@@
 To overcome these barriers, we implemented IoT-enabled data marketplace and sensor data submission functionalities which are intended to be very lightweight and capable of running on embedded devices.
-They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
+They will only need to perform essential operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.
 This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
-\begin{enumerate}
-    \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
-    \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
-    \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
-\end{enumerate}
 

### 2019-10-24 paper.tex
Modify trading model and remove figures

@@
 While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
-See Figure \ref{fig:launching_product}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
 
@@
 \subsection{Launching and Searching Products}
-To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}.
+To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance.
 The data provider determines a trusted broker and asks the broker to create a new MAM channel and product contract.
@@
 Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers.
-Figure \ref{fig:key_certification} shows the certification process.
 When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{key_certification}
-    \caption{Session key certification process with blind signature.}
-    \label{fig:key_certification}
+    \includegraphics[width=0.5\textwidth]{key_certification_exchange}
+    \caption{Session key certification with blind signature and session key exchange.}
+    \label{fig:key_certification_exchange}
 \end{figure}
@@
 \subsection{Trading}
-The entire trading process is as shown in Figure \ref{fig:trading_product}.
 Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{trading_product}
-    \caption{The process for the product trading.}
-    \label{fig:trading_product}
-\end{figure}
-
-Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}.
+Next, session key $k$ should be exchanged between the data provider and consumers.
 The data provider can obtain public keys of each consumer from the registration contract.
@@
 Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{key_exchange}
-    \caption{Session key exchange process between the data provider and consumer.}
-    \label{fig:key_exchange}
-\end{figure}
 

### 2019-10-24 paper.tex
Modify broker and trading model

@@
 \subsubsection{Broker}
-Brokers represent data providers and consumers to perform computing tasks as brokers are expected to have higher resource.
-Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace.
-Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel.
+Brokers represent data providers and consumers to deal with the trading process and publish the provider’s data streams as brokers are expected to have higher resource.
 Brokerage fees for each product will be charged by the broker.
@@
 \section{\normalsize\textbf{Trading Model}}
-In the following, we describe the data trading process in detail where we use game theory to ensure the sustainability of our trading model.
-To participate a data marketplace, data providers and consumers have to register first.
-Then data provider can launch its product on the marketplace.
-Once a product is launched, it is searchable and can be subsequently traded.
-The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
-
-The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
-Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.
-
-Refunds are a major issue in our research.
-However, we do not need to take refund as a factor in our game theory model, since in our decentralized data marketplace we use a smart contract to store the subscription fee which will be paid to buy the future data.
-The subscription fee will be paid as new data is transmitted to consumers.
-In other words, the data provider does not need to perform any procedures to transfer subscription fees from his/her own account to consumers' accounts.
-For the same reason, data providers have no responsibility on refunding processing fees charged by the smart contract.
+In the following, we describe the data registration, production launching, product searching and trading process in detail where we use game theory to ensure the sustainability of our trading model.
+The whole process is defined in smart contracts which are easily traceable and irreversible.
 
@@
 Next, session key $k$ should be exchanged between the data provider and consumers.
-The data provider can obtain public keys of each consumer from the registration contract.
 For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract.
-Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
-
-Consumers can obtain the broker's public key on the registration contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker.
+Consumers decrypt the ciphertext from the product contract to obtain the session key $k$ and signature $Sign(k)$.
+Consumers can verify that the signature is valid and the session key is the only one that is certified by the broker.
 Afterward, encrypted data is published to the MAM channel, and consumers can obtain and decrypt it with the session key.
@@
 To refund or withdraw subscription fees from the smart contract, the data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for the transaction fee.
-We assume that only a half of the expected records are published to the MAM channel.
-When $F_{b}$ is 5\%, the data provider and broker can withdraw half of the total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
-For consumers, they can receive half of the subscription fee refunded which should be deducted from the transaction fee.
-
-Considering the situation that one of the consumers requests a refund in the future, when the consumer is disappointed with the data quality, he/she may request a refund.
 

### 2019-10-25 paper.tex
Simplify the wording in general introduction

@@
 As physical assets such as ships, factories, vehicles, farms and buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value.
-This paradigm shift will be more complex to administers, forcing businesses to rethink their competitive play as part of these ecosystems.
 Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models.
-We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
+There are three main barriers to achieving data marketplace:
 \begin{enumerate}
@@
 
-To overcome these barriers, we implemented IoT-enabled data marketplace and sensor data submission functionalities which are intended to be very lightweight and capable of running on embedded devices.
+To overcome these barriers, we implemented IoT-enabled data marketplace and secure data manipulation which are intended to be very lightweight and capable of running on embedded devices.
 They will only need to perform essential operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure.

### 2019-10-25 paper.tex
Content tweak on chap2, 3

@@
 Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making.
-In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
-This approach can efficiently enhance the degree of transparency, as all interactions with smart contracts will be written on-chain.
+In this paper, we propose a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
+This approach can efficiently enhance the degree of transparency, as all contract-oriented interactions will be written on-chain.
 Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform.
-Furthermore, the platform will complete matching, trading and refunding processes without human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
+Furthermore, the platform will complete matching, trading and refunding processes without human intervention, and it also protects the rights of data providers and consumers through trading policies which apply revolutionary game theory to the machine economy.
+
 \begin{IEEEkeywords}
@@
 As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace.
-The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
-Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
+The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
+Thus, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered that the existence of data can be trusted and no longer rely on any third party authority.
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
 Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
@@
 To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.
-
-Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protection and assurance of data integrity from the source with MAM.
-Nevertheless, the platform design is centralized, where new devices require manual approval from the IOTA Foundation to be visible in the marketplace.
+On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided that allows transmission, access, and verification of an encrypted data stream over the Tangle.
+Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} that not only allows putting data on Tangle without any trusted cloud services, but also allows trading on Tangle where privacy and integrity meet with MAM.
+Nevertheless, the platform is centralized, where new devices require manual approval from the IOTA Foundation.
 Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.
@@
 
-The sustainability of IoT economic system was discussed by Dusit Niyato et al.\cite{UtilityStruct}.
-They evaluated the utility structure of data trading and presented a game theory model.
-Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found via game theory and its utility structure.
-However, refund and subscription economies were not mentioned in their work.
-
-Such work proposed different solutions to specific issues of data marketplaces.
-In this paper, we propose an overall design of decentralized data marketplace that handles data integrity and trading procedures such as buyout and subscriptions to future data on a distributed ledger.
+The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
+They evaluated the utility structure of data trading and presented game theory model.
+Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure.
+However, refund and subscription mechanism were not mentioned in their work.
 
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to post participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with registrars, data providers, data consumers and brokers.
 
@@
 \subsubsection{Registrar}
-The registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.
+Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.
 
 \subsubsection{Data Provider}
-Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.
+Data providers generate and preserve streaming data. With the profit through trading process, they can improve the quality and quantity of data.
 
@@
 \subsubsection{Masked Authenticated Messaging}
-IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.
-
-MAM resolves the challenge to publish encrypted streaming data to distributed ledgers.
-It publishes messages encrypted with a \textbf{session key} to the \textbf{channel}, which is a form of transaction where each address can be derived from the previous one.
-Therefore, with each \textbf{channel root}—the first message of a channel and the session key—all data on the channel is accessible.
-
-One can create multiple channels, however, the size of a channel is fixed which is decided before creation.
-Thus data providers need to firstly decide how to distribute data product into MAM channels.
-While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.
+MAM is a second layer data communication protocol built on the feeless and scalable IOTA network.
+It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one.
+In other words, with channel root (a.k.a., the first message of a channel) and its session key, all data becomes accessible and validatable.
+Furthermore, each user can create multiple channels as possible.
 
@@
 The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and with enforcement.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
+All conditions and states established in the contract are enforeced with transparency.
+The appearance of smart contracts meet different requirements of trading pattern.
 
 \subsubsection{Blind Signature}
-There is inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
-Therefore, a blind signature is used to prevent session key copying for such circumstances.
-Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.
+Blind signature\cite{blindSig} is used to prevent the situation that the a broker would stole data if a session key is not encryted.
+In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm.
+The encrypted message, along with the blinding factor, can be later verified with the signer’s public key.
 
 \subsubsection{IPFS}
-Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but is with all IPFS users.
-In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to the IPFS in order to provide users with search capabilities to meet the consumers' need.
+Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is maintained with all IPFS users.
+In our proposed architecture, brokers are responsible for publishing metadata to IPFS, including titles, data provider information and data preview to provide users with searching capabilities.
 
@@
 \subsection{Participant Registration}
-At the beginning, the egistrar creates a registration contract, which maintains all participants' information, including their DID documents and public keys.
+At the beginning, the registrar creates a registration contract, which maintains all participants' information, including their DID documents and public keys.
 Anyone can query participants' public keys.

### 2019-10-25 paper.tex
Revise the wording in abstract

--- 2019-10-25 paper.tex
@@
 In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
-This approach can efficiently enhance the degree of transparency, as all interactions with smart contracts will be written on-chain.
+This approach can efficiently enhance the degree of transparency, as all contract-oriented interactions will be written on-chain.
 Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform.
-Furthermore, the platform will complete matching, trading and refunding processes without human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
+Furthermore, the platform will complete matching, trading and refunding processes without human intervention, and it also protects the rights of data providers and consumers through trading policies which apply revolutionary game theory to the machine economy.
 \begin{IEEEkeywords}

### 2019-10-25 paper.tex
Simplify the wording in abstract again

@@
 Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making.
-In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
+In this paper, we propose a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers.
 This approach can efficiently enhance the degree of transparency, as all contract-oriented interactions will be written on-chain.

### 2019-10-25 paper.tex
Simplify DLT descriptions

@@
 As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace.
-The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
-Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.
+The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
+Thus, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered that the existence of data can be trusted and no longer rely on any third party authority.
 

### 2019-10-25 paper.tex
Modify Participants Registration

@@
 Furthermore, the platform will complete matching, trading and refunding processes without human intervention, and it also protects the rights of data providers and consumers through trading policies which apply revolutionary game theory to the machine economy.
+
 \begin{IEEEkeywords}
@@
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
 Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
@@
 \subsection{Participant Registration}
-At the beginning, the egistrar creates a registration contract, which maintains all participants' information, including their DID documents and public keys.
-Anyone can query participants' public keys.
-Those who would like to sell or purchase data may register to become a data provider or consumer.
-The registrar has the authority to agree with applications.
-After that, their identities are available in the registration contract and the launching and trading processes can begin.
+At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys.
+Everyone can query others' public keys for validation but only registrars have permission to add new members.
+After registration, the launching and trading processes can begin.
 

### 2019-10-25 paper.tex
Tweak wording

@@
 \begin{IEEEkeywords}
-    streaming data, crowd sensing, data marketplace, decentralization
+    streaming data, crowd sensing, data marketplace, decentralization, blockchain
 \end{IEEEkeywords}
@@
 \section{\normalsize\textbf{Related Work}}
-As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace.
+As the economic value of huge amounts of data emerges, people have started to explore the design of data marketplaces.
 The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data.
@@
 
-Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Data Integrity as a Service (DIaaS) is a DLT-based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
 Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
@@
 Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
-The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
 All conditions and states established in the contract are enforeced with transparency.
@@
 We employed repeated games to build our game theory model.
-Repeated games consists of several repetitions of the same base game which meets the scenario of data subscription.
+Repeated games fits the scenario of data subscription.
 

### 2019-10-25 paper.tex
Simplify the wording around DIaaS

@@
 
-Data Integrity as a Service (DIaaS) is a DLT-based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
-Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization.
-However, the architecture of DIaaS needs high trust on the CSS.
-If the CSS is malicious or has crashed, losses to both providers and consumers will result.
-Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.
+Data Integrity as a Service (DIaaS)\cite{DIaas} is a DLT-based framework for data integrity whichs deploys a Cloud Server Service (CSS) for both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers.
+Its contract can also realize the purchase agreement including authorization and penalization.
+However if the CSS is malicious or has crashed, losses to both providers and consumers will happen.
+Also, performance analysis shows that IoT devices are inefficient to interact with Ethereum due to the time-consuming Proof-of-Work(PoW) operations.
 

### 2019-10-25 paper.tex
Reword trading model

@@
 \subsubsection{Registrar}
-Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.
+Registrars have access to create and maintain registration contracts, a lookup table of participants in decentralized data marketplace.
 
@@
 Brokers certify session keys as well.
-Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers.
-When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded.
-Then the data provider sends the blinded session key $Blind(k)$ to the broker.
-The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider.
-The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.
+Only one session key can be signed for each product, so data providers cannot fake a session key to deceive consumers.
+To certify a session key $k$, the data provider first blinds the session key with broker's public key from registration contract and sends $Blind(k)$ to the broker.
+The broker signs it and returns the signature $Sign(Blind(k))$ back, then the data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.
 
@@
 The contract address and product description will be stored in a file which is uploaded to IPFS.
-Consumers can search the desired product by keywords or tags.
-The consumer then evaluates the product and initiates the trading with the data provider if the consumer is interested in subscribing to the data.
+Consumers can search the desired product by keywords or tags and then launch a trading process for interested products.
 
 \subsection{Trading}
-Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.
+Once a consumer subscribe to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.
 
 Next, session key $k$ should be exchanged between the data provider and consumers.
-For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract.
-Consumers decrypt the ciphertext from the product contract to obtain the session key $k$ and signature $Sign(k)$.
-Consumers can verify that the signature is valid and the session key is the only one that is certified by the broker.
-Afterward, encrypted data is published to the MAM channel, and consumers can obtain and decrypt it with the session key.
+For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the purchase contract.
+Consumers can decrypt $Encrypt(k + Sign(k))$ to obtain and verify the session key $k$ and signature $Sign(k)$.
+Afterward, consumers can access data with session key on the MAM channel.
 
@@
 \subsection{Game Theory Evaluation}
-Game Theory is a methodology to discuss strategic interaciton among game players.
+Game Theory is a methodology to discuss strategic interaction among game players.
 If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace.

### 2019-10-25 paper.tex
Reword game theory

@@
 \subsubsection{Registrar}
-Registrars have access to create and maintain registration contracts, a lookup table of participants in decentralized data marketplace.
+Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.
 
@@
 Only one session key can be signed for each product, so data providers cannot fake a session key to deceive consumers.
-To certify a session key $k$, the data provider first blinds the session key with broker's public key from registration contract and sends $Blind(k)$ to the broker.
+To certify a session key $k$, the data provider first blinds the session key with broker's public key from Registration Contract and sends $Blind(k)$ to the broker.
 The broker signs it and returns the signature $Sign(Blind(k))$ back, then the data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.
@@
 \subsection{Trading}
-Once a consumer subscribe to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.
+Once a consumer subscribes to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.
 
@@
 Game Theory is a methodology to discuss strategic interaction among game players.
-If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace.
-Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing.
-We employed repeated games to build our game theory model.
-Repeated games fits the scenario of data subscription.
+We can ensure the sustainability of decentralized data marketplace by proving the existence of Nash Equilibrium at a certain acceptable range.
+Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our game theory model.
 
@@
 
-According to \textbf{assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational.
-
-\textbf{Assumption(\ref{monopoly})} implies there is no other data providers providing the same product in the data marketplace.
-In this way, we can consider each provider's behavior independently.
-That means this decision tree represents the behavior of only one data provider.
-
-From \textbf{assumption(\ref{51_in_group})}, we derive that one of any consumer in that group launches voting for stopping buying data (in other words, the consumer announces the data quality is not acceptable), they would succeed in rejecting the processing subscription.
-
+According to \textbf{Assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational.
+\textbf{Assumption(\ref{monopoly})} implies each product is unique in the data marketplace.
+Therefore, each provider's behavior independently and the decision tree represents the behavior of only one data provider.
+From \textbf{Assumption(\ref{51_in_group})}, we derive that any consumer in that group launches voting for refund (i.e., the consumer announces the data quality is not acceptable) would succeed.
 \textbf{Assumption(\ref{1_in_51})}  implies if unacceptably low accuracy data are delivered to consumers, the examiner will spread this information out.
 
-Based on the description above, the discounted sum of payoff for our repeated game is
+Based on the assumptions above, the discounted sum of payoff for our repeated game is
 \begin{equation} \label{payoff}
@@
 (\ref{payoff}).
-We can derive an equation illustrating the market mechanism of the subscription trading policy we used under the decentralized data marketplace.
+We can derive an equation illustrating the market mechanism of the subscription trading policy in the proposed decentralized data marketplace.
 First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data.
-Second the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost.
-Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
+Second, the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost.
+Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high data quality under our assumptions.
 
@@
 The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers.
-While there has been many auction models\cite{BigPicDataMarket} in several areas, there has been minimal research on third-party auction platforms.
+While there has been many auction models\cite{BigPicDataMarket} in several areas, only minimal research focus on third-party auction platforms.
 Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers.
-However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved.
-For the game theory model presented in this work, we assume each data provider's behavior is independent.
-However, normally there would be multiple data providers providing similar products (substitutions).
-Only one provider is taken into considerations at present.
+However, the auction process between multiple participants, analysis of potential threats and an overall game theory evaluation are still critical issues that need to be resolved.
 

### 2019-10-25 paper.tex
Update keyword listing
Revise related work

--- 2019-10-25 paper.tex
@@
 \begin{IEEEkeywords}
-    streaming data, crowd sensing, data marketplace, decentralization, blockchain
+    streaming data, data integrity, data marketplace, decentralization, blockchain
 \end{IEEEkeywords}
@@
 
-To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction.
-On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided that allows transmission, access, and verification of an encrypted data stream over the Tangle.
-Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} that not only allows putting data on Tangle without any trusted cloud services, but also allows trading on Tangle where privacy and integrity meet with MAM.
+Targeting IoT industry, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency based on a revolutionary DLT, the \textbf{Tangle}, which has zero transaction fees and the potential for scalability.
+On top of Tangle network, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, allows transmission, access, and verification of an encrypted data stream.
+Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} prototype that not only allows putting data on Tangle without any trusted cloud services, but also enables trading on Tangle where privacy and integrity meet with MAM.
 Nevertheless, the platform is centralized, where new devices require manual approval from the IOTA Foundation.
@@
 
-A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned.
-The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers.
+A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts which consist of providers, consumers and brokers.
 The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.

### 2019-10-26 paper.tex
Tweak related work

@@
 
-A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts which consist of providers, consumers and brokers.
+A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts to interact with providers, consumers and brokers.
 The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers.
@@
 
-The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}.
+The sustainability of IoT economic system was discussed by Dusit Niyato et al.\cite{UtilityStruct}.
 They evaluated the utility structure of data trading and presented game theory model.
 Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure.
-However, refund and subscription mechanism were not mentioned in their work.
+However, refund and subscription mechanism were not mentioned in the original work.
 
 \section{\normalsize\textbf{System Architecture}}
-Our proposed data marketplace framework is a 3-tier decentralized architecture with registrars, data providers, data consumers and brokers.
+Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to post participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.
+Data integrity is enforced with the root of trust built on top of distributed ledgers for transparency and traceability.
 

### 2019-10-26 paper.tex
Tweak wording

@@
 \subsubsection{Broker}
-Brokers represent data providers and consumers to deal with the trading process and publish the provider’s data streams as brokers are expected to have higher resource.
+Brokers represent data providers and consumers to deal with the trading process and publish the provider's data streams as brokers are expected to have higher resource.
 Brokerage fees for each product will be charged by the broker.
@@
 \subsubsection{Masked Authenticated Messaging}
-MAM is a second layer data communication protocol built on the feeless and scalable IOTA network.
+MAM is a second layer data communication protocol built on the IOTA peer-to-peer network infrastructure, the Tangle.
 It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one.
@@
 \subsubsection{Ethereum Smart Contract}
-Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
+Smart contract is a protocol for formulating agreement on a DLT/blockchain that provides verification and execution of the contract.
 All conditions and states established in the contract are enforeced with transparency.
@@
 In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm.
-The encrypted message, along with the blinding factor, can be later verified with the signer’s public key.
+The encrypted message, along with the blinding factor, can be later verified with the signer's public key.
 
@@
 We can ensure the sustainability of decentralized data marketplace by proving the existence of Nash Equilibrium at a certain acceptable range.
-Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our game theory model.
+Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our model.
 

### 2019-10-26 paper.tex
Append conclusion

@@
 
-\section{\normalsize\textbf{Future Work}}
-%Data Auction
+\section{\normalsize\textbf{Conclusion and Future Work}}
+To our knowledge, this paper is the first attempt to construct fully decentralized data marketplaces with strong data integrity and transparency in mind.
 The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers.
-While there has been many auction models\cite{BigPicDataMarket} in several areas, only minimal research focus on third-party auction platforms.
+While there have been various auction models\cite{BigPicDataMarket} in several areas, only few researches focus on third-party auction platforms.
 Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers.

### 2019-10-29 paper.tex
Eliminate the listing of keywords to 4 to fit guidelines
WIP

@@
 \begin{IEEEkeywords}
-    streaming data, data integrity, data marketplace, decentralization, blockchain
+    streaming data, data integrity, data marketplace, decentralization
 \end{IEEEkeywords}
@@
 
+\section{Results}
+Mask Authenticated Messaging (MAM) is the most important component to ensure the data integrity and privacy in our architecture, and it is C library developed by IOTA Foundation.
+
 \section{\normalsize\textbf{Conclusion and Future Work}}
